### 2024-11-14 paper/paper.tex
为规则提供获取对象的多种方式（获取tag 获取引用，获取对象本身，不获取） 添加了log
添加了论文

添加了协议

untagged 暂未完善

\documentclass[9pt,a4paper,twoside]{article}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{svg}

\title{
    Augmented general P systems and high efficiency emulation
    \footnote{
        This work is licensed under CC BY-SA 4.0. To view a copy of this license, visit 
        https://creativecommons.org /licenses/by-sa/4.0/
    }
}

\date{2024-11-11 Draft}
\author{JunShuang Hu\footnote{croteco@outlook.com}}

\begin{document}
    \maketitle
    \pagenumbering{arabic}

\begin{abstract}
    todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo todo 
\end{abstract}
\keywords{Membrane Computing, P Systems, Emulation}

\section{Introduction}

    Based on behaviors of organism in the cell's level, a novel kinds of computing model was formulated. Separation of areas by membranes,
    transportation of matters across membranes and biochemical reactions in membranes are the three important behaviors of cells. 
    These behaviors are captured in symbolic way to crate P systems which transform those behaviors into basic elements for general computing.

    ...  
    todo
    ...

\section{Purpose of Research}
    Since the very first definition of P system, numerous P systems are defined, some introduced new forms of objects and rules, 
    some designed new representation of membrane. They expanded P system's application ares, enhanced P systems' computing ability.

    Nevertheless, the existing researches mostly focused on improving P systems, rather than the definition of P systems.

    This paper provided an augmented general way of define P systems with object expanding, object subdivision, cross system 
    reusing and rule polymorphism. These methods makes it easier to design and define P systems in a more concise way, especial 
    when abstracting from some complex biological behaviors.

    Design of P systems needs verification, if the designed system is too complex, step-by-step verification manually could be 
    frustrating, hence computer emulation of P system could be helpful in P system design verification.

    Some P systems are build for current applications. In the help of P system's structural advantage, like other biology inspired 
    systems, P systems implemented on modern silicon based computers could be powerful in certain application areas, thus having a emulation tool
    will reduce the time and energy of implementing these systems.

    The existing emulation tools and libraries are not high efficient or efficient but not general. 
    This paper provided a novel membrane computing library which is efficient and general for implementing the emulator for varies kind of P systems.

\section{Augmented general P system}

\subsection{Objects}

    Objects definition is in a more refined way in augmented general P system, such consideration is called object subdivision. We use untagged objects in
    situations that rules only care about objects of some types, and use tagged objects when individual objects matters. This is under the inspiration of 
    biochemical reactions of different types.
\subsubsection{Tagged Objects}

        In a augmented general P system tags are used to distinguish different objects of a certain type. 
        A tagged object is defined as $o = (ty, tg)$ where $ty \in S_y, tg \in S_g$ and $S_y, S_g$ are sets of strings on alphabet $A_y, A_g$ separately. 
        $ty$ denotes the type of this object and $tg$ is the tag for this object in its type.

        e.g. chromosome $o_1 = (\text{"Human Chromosome"}, 22)$ 
        and $o_2 = (\text{"Human Chromosome"}, 1)$
\paragraph{Uniqueness of tagged objects:}

                For two objects $o_1 = (ty_1, tg_1)$ and $o_2 = (ty_2, tg_2)$, we say $o_1$ and $o_2$ are the same object if and only if 
                $ty_1 = ty_2$ and $tg_1 = tg_2$.
\paragraph{Objects of the same type:}

                For two objects $o_1 = (ty_1, tg_1)$ and $o_2 = (ty_2, tg_2)$, we say $o_1$ and $o_2$ are of the same type if and only if 
                $ty_1 = ty_2$.
\paragraph{Unique properties of tagged objects:}

                Because every tagged objects are different, there could be some unique properties for a certain object that affect how rules could be 
                applied, these properties can be used to simplify the design of rules which abstracted from behaviors like gene expression or protein functioning.

                The properties $p$ of object $o$ is defined as $p = Property(o)$, where $Property: O_t \rightarrow P$, $O_t$ is a set of tagged objects,
                $P$ is the power set of the union of sets $S_1, S_2,...,S_n$, $S_1, S_2,...,S_n$ represent different kinds of properties .

                e.g. for
                $o_1 = ($"protein"$, 1)$,
                $o_2 = ($"protein"$, 2)$,
                $Property(o_1) = \{$"has glycine"$,$"10 amino acids"$,42\}$,
                $Property(o_2) = \{$"has leucine"$,$"20 amino acids"$,233\}$

                This allows to express almost anything related to a certain object further used by rules.

\subsubsection{Untagged Objects}

            Untagged objects are more like the original definition of objects in previous P systems.
            Untagged objects are described as a type of objects, an untagged object is defined as $u = ty$ where $ty \in S_y$ and $S_y$ is a set of strings on alphabet $A_y$.

            It is useful when designing rules for a type of objects like the rule from proteolysis in which case the differences of each protein are out of concern.
            Untagged objects ignores the difference of objects of the same type. e.g. carbohydrate $u_1 = \text{"Galactose"}$ and $u_2 = \text{"Glucose"} $
\paragraph{Amount of untagged objects:}

                    Let $Amount: O_u \rightarrow \mathbb{R}$ be the mapping of the amount of a untagged object from $O_u$.
                    Let $a_{ty} = Amount_\omega(ty)$ be the amount of object of type $ty$ in region $\omega$, where $\omega \in S$ and $Amount_\omega: S_y \rightarrow \mathbb{R}$, 
                    $S$ and $S_y$ are sets of strings. The following equation is always satisfied.
                    \begin{equation}
                        \begin{align}
                            a_{ty} &= Amount_\omega(ty) \\
                            &= \sum_{o \in O'}{Amount(o)} \\
                        \end{align}
                    \end{equation}
                    where $O' = \{ o_i = ty_i \mid o_i \in O_u, o_i\text{ is in region }\omega, ty_i = ty \} $. This is equivalent to the expression with multi-set of 
                    untagged objects in a region, where the multitude of each object is a real number which corresponding to the amount of objects in a region.

\paragraph{Untagged reference of tagged object}

                    Let $Amount_t: O_t \rightarrow \mathbb{R}$ be the amount of a single tagged object in $O_t$, if not defined, $Amount_t(o) = 1$.
                    For tagged objects $o_1, o_2,...,o_n, n \in \mathbb{N}^+$ and $a_i = Amount_t(o_i)$, where $o_i = (ty, tg_i)$ and pair $p_i=(o_i, a_i)_{amount}$ 
                    of mapping $Amount_t$ satisfies $p_i \in Property(o_i)$ for $1 \leq i \leq n$.

                    Let $a = \sum{a_i}$, the untagged reference of $o_1, o_2, ..., o_n$ is $u_r = ty$ with $Amount(u_r) = a$. $o_1, o_2, ..., o_n$ are called
                    the original objects of $u_r$. Note that the original objects of a untagged reference is not unique.

                    Untagged objects are like small molecules while tagged objects are like macromolecules. Conditions with untagged objects usually correspond to the
                    statistical characteristics of small molecules, like concentration, while tagged objects are for reactions in molecule level, like gene expressions.
                    They represent real life objects in different scales, the untagged reference is a bridge between them, allows the same object to be used in different
                    scale.

                    Note that $Amount_t$ is not the "amount of this tagged object", rather, it is "the amount the untagged object that this tagged object turned into".
                    Due to the uniqueness of tagged objects, "the amount of this tagged object" should always be one across all regions.

\subsection{Rules}

    A rule $r$ is in the form of $r: c \rightarrow e_c$, $c \in C_O$ is called the condition of $r$ and $e_c \in E_c$ is called the effect of $r$ under its
    condition $c$, $C_O$ is a set of conditions on objects $O$ and $E_c$ is a set of effects under condition $c$.

\paragraph{Tagged reference of rule}

            For a rule $r: c \rightarrow e_c$ in region $\omega$, it can be seen as a tagged object $o_r = (r, \omega)$ with $(c \rightarrow e_c) \in Property(o_r)$
            or vice versa. $o_r$ is then called the tagged reference of $r$, and $r$ is called the original rule of $o_r$. When there's no confusion, $r$ and $o_r$
            can share a same symbol.

            For clarity of expression, the variable parts of the rule's condition and effect should be written as variables along with the rule definition. Let
            $a_1, a_2,..,a_n$($n \geq 1$) be the variable of rule $r$, $r$ is defined as $r(a_1, a_2,...,a_n): c \rightarrow e_c$.
            Further, $a_i \in Property(o_r), 1 \leq i \leq n$

            Once rules are taken as objects, they can be modified by other rules, or itself, this brings more flexibility to the system. For example in a spiking neural  
            P system with dynamic threshold, each time the fire rule has been applied, the threshold of the fire rule will be changed. Therefore the condition of firing
            rule is not static, but its original definition implicitly used this concept. In augmented general P systems, this mutability must be used explicitly with
            tagged references for a clear and unified expression.

\subsubsection{Conditions}

            Let $C_u = \{(u, a) \mid u \in O_u \cup O_{ru}, a \in \mathbb{R}\}$ where $O_u$ is a set of untagged objects and $O_{ru}$ is a set untagged references.
            Let $C_t = O_t \cup O_{rt}$ where $O_t$ is a set of tagged objects and $O_{rt}$ is a set tagged references.
            The set of conditions on $O = O_t \cup O_u$ is $C = \{(c_t, c_u) \mid c_t \subseteq C_t, c_u \subseteq C_u\}$ 
            where $O_t$ is a set of tagged objects and tagged references.

\paragraph{Determined condition and non-determined condition}
            Condition $c=(c_t, c_u)$ is a determined condition if and only if there is no untagged references in
            $c_u$, else it is a non-determined condition.

            A rule with non-determined condition requires the region to have a certain amount of tagged objects of some types, 
            but the exact objects used for this rule is chosen in a non-determined way.

            e.g. 
            $c_1 = (\{o_{t1}, o_{t2}\}, \{(u_1, 10.0), (u_2, 5.0)\})$ for tagged objects $o_{t1}, o_{t2}$ and untagged objects $u_1, u_2$,
            or more realistically
            $c = (\{ o_1=($"protein"$,$ $1)$ $,$ $ o_2=($"protein"$,$$ 2) \}$ $,$ $ \{(u_1=$"temperature" $,$
            $40)$ $,$ $ (u_2=$"pH"$,$$ 8.1)\})$.

\subsubsection{Effects}

            The set of all effect under condition $c=(c_t, c_u)$ is $E_c = \{ f_c \mid f_c: P(O_c) \rightarrow P(I) \}$  where $P(O_c)$ is the power set of 
            $O_c$, $O_c = \{o \mid o \in c_t \vee o \in c_u\}$. $P(I)$ is a power set of influences $I$.

            Influences describe how a region acts under an effect, for the sack of generality, they are not strictly defined. 
            Depends on the type of the membrane that defines the region, influences may be interpreted differently, this feature is called rule polymorphism.

            Across all membranes, the following types of influences are always recognizable, namely, they are universal influences.
\paragraph{Universal influences:}

                A universal influence $i \in I_U$ is defined as $i = (op, (o,a))$, where $op \in \{\text{"Add"}$ $,$ $ \text{"Remove"}, \text{"Stop"}\}$$,$$ o \in O_t \cup O_u \cup \{\epsilon\}$,
                $a \in \mathbb{R} \cup \{\epsilon\}$ is the amount of the object to be removed, $O_t$ is a set of tagged objects, and $O_u$ is a set of untagged objects, 
                $\epsilon$ denotes no object or amount is required.

                If $a = \epsilon$ then $i$ can be written as $i = (op, o)$, if $a = \epsilon$ and $o =\epsilon$,  $i$
                can be written as $i=op$. 
\begin{itemize}
                \item "Add" insists the object $o$ to be added to the region $\omega$ where the rule is applied. 
                    If $a \neq \epsilon$, 
                        when $o$ is tagged, $Amount_t(o) = a$ is added to $Property(o)$, 
                        when $o$ is untagged, $Amount_\omega(o) = a$ is added to region $\omega$.

                    If $o$ already exists in $\omega$,
                        when $o$ is tagged, the existing object is replaced, for convenience, changes of properties of $o$ can be marked after
                        its symbol as $o(p_1 = p_1', p_2 = p_2',..., p_n = p_n')$
                        when $o$ is untagged, $a_{old} = Amount_\omega(o)$ is replaces by $a_{new} = a_{old} + a$.

                    For untagged object, $a$ can not be $\epsilon$.

                \item "Remove" insists the object $o$ to be removed in the region where the rule is applied, $o$ must be in the condition of the rule, $a$ is ignored.

                \item "Stop" insists the region where the rule is applied to stop evolving, $o$ must be $\epsilon$.
\end{itemize}

            e.g. for rule $r: c \rightarrow e_c$, $c = (\{ o_1=(\text{"protein"}, \text{'a'}) \}, \{(u_1=\text{"enzyme"}, 10)\})$, 
            $e_c = \{ (\{o_1\}, \{(\text{"Remove"}, o_1)\})\} $

            An effect for a rule is a mapping over a subset of objects in the rule's condition to a set of influences.

\paragraph{Satisfaction of rules and applying rules:}

                For a rule $r: c \rightarrow e_c$ in region $\omega$, $c = (c_t, c_u)$, we call this rule is satisfied in $\omega$ if and only if 
                $\forall o_t \in c_t$ $,$ $ \forall (o_u, a_u) \in c_u$ $,$ $o_t \in O_{\omega}, o_u \in O_{\omega} \text{ and } Amount_\omega(o_u) \geq a_u$.

                If rule $r$ is satisfied in region $\omega$, then to apply $r$ in $\omega$ is to calculate the effect mapping $e_c$ to get influences $i$,
                and region $r$ uses $i$ to update itself.

                If the condition of a rule is empty, then the rule is always satisfied. If the effect of a rule is empty, then the rule produces no influence.

\subsubsection{Simplified notations}

            For rule $r(a_1,a_2,...a_n): c \rightarrow e_c$, where $c=(c_t, c_u)$, the simplified rule expression is:
            \begin{equation}
                \begin{align}
                    &r(a_1,a_2,...a_n): \\
                    &c_1 \rightarrow e_c(c_1)  \\
                    &c_2 \rightarrow e_c(c_2)  \\
                    &...\\
                    &c_n \rightarrow e_c(c_n)  \\
                \end{align}
            \end{equation}
            or in a single line
            \begin{equation}
                r(a_1,a_2,...a_n): c_1c_2...c_n \rightarrow e_c(c_1)e_c(c_2)...e_c(c_n)
            \end{equation}
            where
            \begin{equation}
                \bigcup_{k = 1}^{n}{c_k} = c_t \cup c_u, \bigcap_{k = 1}^{n}{c_k} = \emptyset
            \end{equation}

            Then, $c_k = \{o_{k1},o_{k2},...,o_{kp}\} \cup \{(u_{k1},a_{k1}), (u_{k2},a_{k2}),..., (u_{kq},a_{kq})\}$ for $1 \leq k \leq n$ can be written as 
            $o_{k1}o_{k2}...o_{kp}(u_{k1}, a_{k1})(u_{k2}, a_{k2})...(u_{kq}, a_{kq})$.

            If $i_k = e_c(c_k)$ are universal influences $\{ (op_1, (o_1,a_1)), (op_2, (o_2,a_2)),...,(op_m, (o_m,a_m))  \}$, 
            $i_k$ can be written as $op_1(o_1, a_1)op_2(o_2, a_2)...op_m(o_m, a_m)$

            e.g. 
            \begin{equation}
                \begin{align}
                    &r_1: \\
                    &o_1o_2(u_1, 10) \rightarrow \text{Remove}(o_1)\text{Add}(u_1, 5)  \\
                    &o_3 \rightarrow \text{Add}(o_4) \\
                    &(u_2, 20) \rightarrow \epsilon \\
                \end{align}
            \end{equation}
            or
            \begin{equation}
                \begin{align}
                    &r_2(a): \\
                    &(u_1, a) \rightarrow \text{Remove}(u_1) \\
                    &r_2 \rightarrow \text{Add}(r_2(a = a + 1))
                \end{align}
            \end{equation}
            or
            \begin{equation}
                \begin{align}
                    r_3: o_1o_2(u_1, 60) \rightarrow \text{Add}(o_3)\text{Remove}(o_2)
                \end{align}
            \end{equation}
            or
            \begin{equation}
                \begin{align}
                    r_4:\epsilon \rightarrow \text{Add}(o_1)\text{Add}(u_1, 1.1)
                \end{align}
            \end{equation}

            $\epsilon$ denotes no condition or effect required.
            This allows to implement a very complex behavior in one rule.

\subsection{Membranes}

        In augmented general P systems, a membrane $m$ is defined as $m=(\omega, O_s, R_s, F)$ where $F = (Check^*, Apply^*, Deref_u^*, Deref_t^*, Evolve)$ is the feature tuple of $m$ (or feature for short), $\omega$ is the region defined by $m$, $O_s$ and $R_s$ are objects and rules in $m$.
        Let $O = O_t \cup O_u \cup O_{rt} \cup O_{ru}$ be the set of all possible objects, let $R$ be the set of all possible rules and let $I$ be the set
        of all recognizable influences.

        Different types of membranes may have different behaviors or strategies and corresponding to the different feature tuples. Feature tuple decides how a region under a specific membrane should evolve, 
        behaviors of a membrane is abstracted into the following mappings.

    \begin{itemize}
        \item  $Check: (R, P(O)) \rightarrow \{yes, no\}$ is a mapping a rule and a set of objects to a result of $yes$ or $no$, representing the
        the membrane's logic of decide whether a rule can be applied or not on a set of existing objects in a region.

        \item  $Apply: (I, P(O)) \rightarrow P(O)$ is a mapping from an influence and a set of objects to a set of updated objects,
        it represents the rule's logic on handling an influence on a set of objects.

        \item $Deref_u: (O_{ru}, \mathbb{R}) \rightarrow P(O_t)$ represents the logic of the membrane on decide the original objects of a untagged reference
        of a certain amount.

        \item $Deref_t: O_{rt} \rightarrow R$, represents the logic of the membrane on decide the original rule of a tagged reference.

        \item $Evolve: (P(O), P(R)) \rightarrow (P(O), P(R))$ defines how this membrane is evolving in each iteration.

    \end{itemize}

        For a feature tuple, only $Evolve$ mapping is required, other mappings are optional and marked with "$*$".
        When processing influences, the following two actions can be done automatically.

    \begin{itemize}
        \item Before the effect calculation, if an object is a untagged reference, it will be mapped into tagged objects with $Deref_u$ with the same amount.
        \item After $Apply$ mapping, if an object is a tagged reference, it will be mapped into a rule with $Deref_t$, and the corresponding rule is added or removed. 
    \end{itemize}

\subsubsection{Default scheme of $Evolve$}
        Mapping $Evolve$ can be defined in any form depending on the requirement of the specific system. Default scheme of $Evolve$ gives an optional default infrastructure for systems that build upon augmented general P system, as showing in table 1.
\begin{table}[ht]
\centering
\begin{tabular}{ll}
\hline
Step & Actions           \\ \hline
1    & aaaaaaaaaaaaaaaaaaaaaa \\
     & aaaaaaaaaaaaaaaaaaaaaaaaaaaaaa\\
2    & aaaaaaaaaaaaaa    \\
3    & aaaaaaaaaaaaa     \\ \hline
\end{tabular}
\caption{Default $Evolve$ mapping }
\label{tab:my-table}
\end{table}

\subsubsection{Region notations}
    A region $\omega$ defined by membrane $m=(\omega, O_s, R_s, F)$ can be written as the 
    following string representation if needed.
    \begin{equation}
        \omega: [ o_1o_2...o_n \mid r_1r_2...r_m ]_F
    \end{equation}
    where $O_s = \{ o_1, o_2,...,o_n \}$ and $R_s = \{r_1,r_2,...,r_m\}$, "$[$ $]_F$" represents the membrane that defines this region with feature $F$. Or with graph representation in figure 1.
    \begin{figure}[ht]
        \centering
        \includesvg{./figures/placeholder.svg}
        \caption{Graph representation of a region}
        \label{fig:enter-label}
    \end{figure}

\subsection{Cross system reusing}

\section{High efficiency emulation for augmented general P system}

\section{Other elements}

%----------------------------------------------------------

\printbibliography

%----------------------------------------------------------

\end{document}

### 2024-11-14 meme_derive/src/lib.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 extern crate proc_macro;
 
 use std::borrow::Borrow;

### 2024-11-14 src/core.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use ahash::{AHashMap, AHashSet};
 use krnl::scalar::Scalar;
 use rand::seq::IteratorRandom;
@@ -6,10 +7,13 @@ use rand::seq::SliceRandom;
 use crate::errors::MemError;
 use crate::helpers;
 use crate::lib_info::log_target;
+use crate::rules::BasicCondition;
+use crate::rules::BasicEffect;
 
 use std::any::Any;
 
 use std::any::TypeId;
+use std::collections::VecDeque;
 use std::fmt::Debug;
 use std::hash::Hash;
 use std::sync::Arc;
@@ -18,15 +22,18 @@ use log::{log, Level};
 pub type IntoSRStr = dyn Into<&'static str>;
 pub type PObj<T, U = u32> = Box<dyn IObj<Tag = T, Unit = U> + Send + Sync>;
 pub type ArcObj<T, U = u32> = Arc<dyn IObj<Tag = T, Unit = U> + Send + Sync>;
-pub type PRule<T, OT, U, OU, E, C> = Box<dyn IRule<Tag = T, ObjTag = OT, Unit = U, ObjUnit = OU, Effect = E, Condition = C> + Send + Sync>;
+pub type PRule<T, OT = T, U = u32, OU = U, E = BasicEffect<OT, OU>, C = BasicCondition<OT, OU>> 
+            = Box<dyn IRule<Tag = T, ObjTag = OT, Unit = U, ObjUnit = OU, Effect = E, Condition = C> + Send + Sync>;
 pub type UntaggedPresences<U> = Vec<UntaggedPresence<U>>;
 pub type TaggedPresences<T> = Vec<TaggedPresence<T>>;
 
-pub type ObjsCrateFn<T, U> = fn(&RequestedObj<T, U>) -> Vec<PObj<T, U>>;
-pub type ObjCrateFn<T, U> = fn(&RequestedObj<T, U>) -> PObj<T, U>;
-pub type ObjsRemoveFn<T, U> = fn(&RequestedObj<T, U>) -> Vec<T>;
-pub type ObjRemoveFn<T, U> = fn(&RequestedObj<T, U>) -> T;
+pub type ObjsCrateFn<T, U> = fn(&mut RequestedObj<T, U>) -> Vec<PObj<T, U>>;
[…]

### 2024-11-14 src/errors.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use std::fmt;
 
 pub struct MemError<T> {

### 2024-11-14 src/gpu.rs

@@ -1,4 +1,4 @@
-
+// Copyright 2024 Junshuang Hu
 use krnl::device::Device;
 use log::{log, Level};
 use once_cell::sync;

### 2024-11-14 src/helpers.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use std::hash::Hash;
 use std::sync::atomic::{self, Ordering};
 
@@ -7,7 +8,7 @@ use krnl::scalar::Scalar;
 use log::Level;
 use log::log;
 
-use crate::core::{ICondition, IObj, IRuleEffect, ObjCrateFn, ObjRemoveFn, ObjType, ObjsCrateFn, ObjsRemoveFn, OperationEffect, TaggedPresence, TaggedPresences, UntaggedPresence, UntaggedPresences};
+use crate::core::{ICondition, IObj, IRuleEffect, ObjCrateFn, ObjRemoveFn, ObjType, ObjsCrateFn, ObjsRemoveFn, OperationEffect, TaggedPresence, TaggedPresences, UntaggedPresence, UntaggedPresences, UseBy};
 use crate::gpu;
 use crate::lib_info::log_target;
 
@@ -112,7 +113,7 @@ impl<T: Clone + Hash + Eq, U: Scalar> ConditionBuilder<T, U> {
     /// 选取指定tag的对象
     pub fn the_tagged(mut self, tag: T) -> Self {
         let otg = self.of_tag.get_or_insert(Vec::new());
-        otg.push(TaggedPresence::of_tag(tag, false));
+        otg.push(TaggedPresence::of_tag(tag, UseBy::None));
         self.last_added_is_otg = true;
         self
     }
@@ -121,7 +122,7 @@ impl<T: Clone + Hash + Eq, U: Scalar> ConditionBuilder<T, U> {
      pub fn some_tagged(mut self, tags: Vec<T>) -> Self {
         let otg = self.of_tag.get_or_insert(Vec::new());
         for t in tags {
-            otg.push(TaggedPresence::of_tag(t, false));
+            otg.push(TaggedPresence::of_tag(t, UseBy::None));
         }
         self.last_added_is_otg = true;
         self
@@ -149,43 +150,57 @@ impl<T: Clone + Hash + Eq, U: Scalar> ConditionBuilder<T, U> {
     /// ```
     pub fn rand_tagged<Obj: IObj + 'static>(mut self, count: usize) -> Self {
         let otg = self.of_tag.get_or_insert(Vec::new());
-        otg.push(TaggedPresence::rand_tags((ObjType::new::<Obj>(&crate::core::DEFAULT_GROUP), count), false));
[…]

### 2024-11-14 src/lib.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 pub mod core;
 pub mod lib_info;
 pub mod errors;

### 2024-11-14 src/lib_info.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 pub fn hello_meme() -> &'static str {
 "
 This is Membrane Emulator lib.

### 2024-11-14 src/mems.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 pub mod basic;
 
 // todo： 膜管理器

### 2024-11-14 src/mems/basic.rs

@@ -1,3 +1,5 @@
+// Copyright 2024 Junshuang Hu
+use crate::lib_info::log_target;
 use crate::rules::BasicCondition;
 use crate::rules::BasicEffect;
 use crate as meme;
@@ -10,6 +12,8 @@ use std::fmt::Debug;
 use std::hash::Hash;
 use std::sync::Arc;
 use std::sync::Mutex;
+use std::time::Instant;
+use log::{log, Level};
 
 use krnl::scalar::Scalar;
 use rand::seq::SliceRandom;
@@ -29,6 +33,7 @@ U: Scalar {
     tag: T,
 
     ready: bool,
+    no_parallel: bool,
 
     objs: BasicObjStore<OT, U>,
     rules: BasicRuleStore<RT, OT, U>,
@@ -42,10 +47,11 @@ OT: Clone + Hash + Eq + Send + Sync + Debug + 'static,
 RT: Clone + Hash + Eq + Send + Sync + Debug + 'static,
 U: Scalar
 {
-    pub fn new(tag: T) -> Self {
+    pub fn new(tag: T, no_parallel: bool) -> Self {
         Self {
             tag,
             ready: false,
+            no_parallel,
             objs: BasicObjStore::new(),
             rules:  BasicRuleStore::new()
         }
@@ -62,28 +68,37 @@ U: Scalar
     }
 
     pub fn effect_proc(
-        es: &Vec<OperationEffect<OT, U>>, req: RequestedObj<'_, OT, U>, stop_mux: &Arc<Mutex<bool>>,
+        es: &Vec<OperationEffect<OT, U>>, mut req: RequestedObj<'_, OT, U>, stop_mux: &Arc<Mutex<bool>>,
         out_to_add: &mut Vec<PObj<OT, U>>, out_to_remove: &mut Vec<OT>) {
         for e in es {
             match e {
+                OperationEffect::CreateObj(f) => {
+                    out_to_add.push(f(&mut req));
+                },
                 OperationEffect::CreateObjs(f) => {
-                    let mut new_o = f(&req);
+                    let mut new_o = f(&mut req);
                     while let Some(o) = new_o.pop() {
                         out_to_add.push(o);
                     }
                 },
                 OperationEffect::RemoveObjs(f) => {
-                    let mut v = f(&req);
+                    let mut v = f(&mut req);
                     while let Some(t) = v.pop() {
                         out_to_remove.push(t);
                     }
                 },
-                OperationEffect::CreateObj(f) => {
-                    out_to_add.push(f(&req));
[…]

### 2024-11-14 src/objs.rs

@@ -1,9 +1,10 @@
+// Copyright 2024 Junshuang Hu
 use std::{any::TypeId, collections::hash_map::Values, hash::Hash};
 
 use ahash::AHashMap;
 use krnl::scalar::Scalar;
 
-use crate::core::{IObjStat, ITaggedStore, IndexMap, PObj};
+use crate::core::{IObjStat, ITaggedStore, IUntaggedStore, IndexMap, PObj};
 
 pub mod com;
 // todo: 分类储存obj
@@ -12,7 +13,7 @@ pub mod com;
 pub struct BasicObjStore<T = u32, U = u32>
 where T: Clone + Hash + Eq, U: Scalar {
     instances: AHashMap<T, PObj<T, U>>,
-    amount: IndexMap<TypeId, U>,
+    amount: IndexMap<TypeId,(U, U)>,
     modified: bool
 }
 
@@ -47,24 +48,23 @@ where T: Clone + Hash + Eq, U: Scalar {
         if let Some(tag_o) = self.instances.remove(t) {
             self.modified = true;
             if let Some(am) = self.amount.get_mut(&tag_o.obj_type().tid) {
-                *am -= tag_o.obj_amount();
+                am.0 -= tag_o.obj_amount();
             }
             return Some(tag_o);
         }
         None
     }
 
-    /// 不失败
     fn add_or_update(&mut self, t: T, v: PObj<T, U>) -> Option<PObj<T, U>> {
         self.modified = true;
         if let Some(am) = self.amount.get_mut(&v.obj_type().tid) {
-            *am += v.obj_amount();
+            am.0 += v.obj_amount();
         } else {
-            self.amount.insert(v.obj_type().tid, v.obj_amount());
+            self.amount.insert(v.obj_type().tid, (v.obj_amount(), U::zero()));
         }
         if let Some(old) = self.instances.insert(t, v) {
             if let Some(am) = self.amount.get_mut(&old.obj_type().tid) {
-                *am -= old.obj_amount();
+                am.0 -= old.obj_amount();
             }
             return Some(old);
         }
@@ -79,49 +79,140 @@ where T: Clone + Hash + Eq, U: Scalar {
         self.instances.values_mut()
     }
     
-    /// 按顺序获取ts中对应tag的value，不存在的会被略过
-    fn get_batch(&self, ts: &[T]) -> Vec<&PObj<T, U>> {
+    fn get_batch(&self, ts: &[T]) -> Vec<Option<&PObj<T, U>>> {
[…]

### 2024-11-14 src/objs/com.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use std::{fmt::Debug, hash::Hash, sync:: Mutex};
 
 use crossbeam_channel::{unbounded, Receiver, Sender};

### 2024-11-14 src/rules.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use std::{any::TypeId, hash::Hash};
 
 use ahash::AHashMap;
@@ -13,7 +14,7 @@ pub mod com;
 //     pub action_obj_gen: Option<>
 // }
 
-#[derive(Debug)]
+#[derive(Debug, Clone)]
 pub struct BasicEffect<T = u32, U = u32>
 where T: Send + Sync, U: Send + Sync {
     effects: Option<Vec<OperationEffect<T, U>>>,
@@ -123,7 +124,7 @@ C: ICondition<OT, OU> {
     }
 
     fn remove(&mut self, t: &T) -> Option<PRule<T, OT, U, OU, E, C>> {
-        let old_ind = self.index_of(t);
+        let old_ind = self.pos_of(t);
         if let Some(old) = self.inner.remove(t) {
             let old_c = self.stat.remove(old_ind.unwrap());
             if let Some(o_req) = old_c.untagged() {
@@ -154,7 +155,7 @@ C: ICondition<OT, OU> {
             }
         }
         if let Some(old) =  self.inner.insert(t.clone(), v) {
-            let ind = self.index_of(&t).unwrap();
+            let ind = self.pos_of(&t).unwrap();
             if let Some(o_req) = old.condition().untagged() {
                 for o in o_req {
                     let a = self.amount.get_mut(&o.ty.tid).unwrap();
@@ -181,13 +182,36 @@ C: ICondition<OT, OU> {
         self.inner.vals_mut()
     }
     
-    fn get_batch(&self, ts: &[T]) -> Vec<&PRule<T, OT, U, OU, E, C>> {
+    fn get_batch(&self, ts: &[T]) -> Vec<Option<&PRule<T, OT, U, OU, E, C>>> {
+        ts.iter().map(|t| self.inner.get(t)).collect()
+    }
+     
+    fn get_batch_skip(&self, ts: &[T]) -> Vec<&PRule<T, OT, U, OU, E, C>> {
         ts.iter().filter_map(|t| self.inner.get(t)).collect()
     }
     
-    fn remove_batch(&mut self, ts: &[T]) -> Vec<PRule<T, OT, U, OU, E, C>> {
-        ts.iter().filter_map(|t| self.inner.remove(t)).collect()
+    fn remove_batch(&mut self, ts: &[T]) -> Vec<Option<PRule<T, OT, U, OU, E, C>>> {
[…]

### 2024-11-14 src/rules/com.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use std::{fmt::Debug, hash::Hash};
 
 use crate::{self as meme, core::{PObj, TypeGroup}, objs::com::{ObjChannel, SendMsg}};
@@ -6,7 +7,7 @@ use meme::{helpers, rules::{BasicCondition, BasicEffect}};
 use meme_derive::{IObj, IRule};
 
 
-/// todo: 改进为无锁实现
+/// todo: 改进为无锁实现?
 #[derive(IObj, Debug, IRule)]
 #[obj_type(TypeGroup::Com)]
 pub struct SendReceiveRule<T, OT, U = u32, OU = u32>
@@ -38,22 +39,22 @@ OU: Scalar
             tag, amount: U::one(), 
 
             cond: helpers::condition_builder()
-            .some_tagged(known_channels)// `n`
-            .rand_tagged::<SendMsg<OT, OU>>(1)//`m`
+            .some_tagged(known_channels).by_ref()
+            .rand_tagged::<SendMsg<OT, OU>>(1).by_ref()
             .build(),
 
             eff: helpers::effect_builder()
             .remove_objs(|req| { // 复杂度 `O(mn)` ，有互斥锁
-                let mo: &PObj<OT, OU> = req.the_rand_tagged(0, 0).unwrap();
-                let cho = req.set.as_ref().unwrap();
+                let mo: &PObj<OT, OU>= req.rand_refs(0).unwrap()[0];
+                let cho = req.refr.as_ref().unwrap().set.as_ref().unwrap();
                 let mut res = Vec::new();
                 let mut done = true;
                 if let Some(msg) = mo.as_any().downcast_ref::<SendMsg<OT, OU>>() {
                     msg.send_msgs.iter().for_each(|w| {
-                        if let Ok(mut wo) = w.obj.lock() { // 如果膜的对象不被外部直接修改，则改锁总是成功
-                            if wo.is_some() {
-                                if let Some(co) = cho.iter().find(|o| *o.obj_tag() == w.channel_t) {
-                                    if let Some(ch) = co.as_any().downcast_ref::<ObjChannel<OT, OU>>() {
+                        if let Some(co) = cho.iter().find(|o| *o.obj_tag() == w.channel_t) {
+                            if let Some(ch) = co.as_any().downcast_ref::<ObjChannel<OT, OU>>() {
[…]

### 2024-11-14 src/rules/persist.rs

@@ -1,1 +1,2 @@
+// Copyright 2024 Junshuang Hu
 //todo

### 2024-11-14 tests/mems/test_mem.rs

@@ -3,7 +3,7 @@ use std::thread;
 
 use meme::{core::IMem, helpers, mems::basic::BasicMem, objs::com::{ObjChannel, SendMsg, SendWrapper}, rules::{com::SendReceiveRule, BasicCondition, BasicEffect}};
 use meme_derive::*;
-use crate::{objs::{TestObjA, TestObjB}, rules::{TestRuleA, TestRuleB}};
+use crate::{objs::{TestObjA, TestObjB}, rules::{TestRuleA, TestRuleB, TestRuleC}};
 
 #[derive(IObj, Debug)]
 pub struct StopObj {
@@ -11,7 +11,7 @@ pub struct StopObj {
     tag: i32
 }
 
-#[derive(IObj, IRule, Debug)]
+#[derive(IObj, IRule, Debug, Clone)]
 pub struct TestRuleStop {
     #[tag]
     tag: u32,
@@ -54,12 +54,12 @@ impl TestComRule {
 
             cond: helpers::condition_builder()
                 .some_untagged::<TestObjB>(1)
-                .the_tagged(to_ch)
+                .the_tagged(to_ch).by_ref()
                 .build(),
 
             eff: helpers::effect_builder()
                 .crate_obj(|req| {
-                    let co = req.the_tagged(0).unwrap();
+                    let co = req.set_ref(0).unwrap();
                     let ct: &i32 = co.obj_tag();
                     let v = vec![
                         SendWrapper::new(Box::new(TestObjA::new(helpers::IdGen::next_i32_id(), 555.555)), ct.clone())
@@ -75,7 +75,7 @@ impl TestComRule {
 
 #[test]
 pub fn basics() {
-    let mut m = BasicMem::<u32, i32>::new(100);
+    let mut m = BasicMem::<u32, i32>::new(100, false);
     let mut ids = Vec::new();
     ids.resize_with(4, || helpers::IdGen::next_i32_id());
     let (ca, cb) = ObjChannel::<i32>::new_pair(ids[2], ids[3]);
@@ -89,8 +89,9 @@ pub fn basics() {
             Box::new(TestRuleA::new(0, ids[0])),
             Box::new(TestRuleB::new(1)),
             Box::new(TestRuleStop::new(2)),
-            Box::new(TestComRule::new(4, ids[2])),
             Box::new(SendReceiveRule::new(3, vec![ids[2]])),
+            Box::new(TestComRule::new(4, ids[2])),
[…]

### 2024-11-14 tests/misc/mod.rs

@@ -1,7 +1,9 @@
 use std::borrow::Borrow;
 
-use meme::core::IndexMap;
+use meme::core::{IndexMap, PObj, PRule};
 use rand::{thread_rng, Rng};
+
+use crate::mems::test_mem::TestRuleStop;
 
 #[test]
 pub fn index_map_test() {
@@ -65,4 +67,14 @@ pub fn vec_batch_remove_test() {
     assert_eq!(res[4], None);
 
     assert_eq!(v, vec![1,3,4]);
+}
+
+#[test]
+pub fn rule_obj_cast_test() {
+    let rule: PRule<u32, i32> = Box::new(TestRuleStop::new(2));
+    let rule_actual = rule.as_any().downcast_ref::<TestRuleStop>();
+    assert!(rule_actual.is_some());
+    let rule_clone = rule_actual.unwrap().clone();
+    let rule_as_obj: PObj<u32> = Box::new(rule_clone);
+    assert!(rule_as_obj.obj_type() == rule.obj_type());
 }

### 2024-11-14 tests/objs/mod.rs

@@ -5,6 +5,18 @@ use meme::core::{IObjStat, ITaggedStore, TypeGroup};
 use meme::objs::BasicObjStore;
 use meme_derive::IObj;
 
+#[derive(IObj, Debug)]
+#[obj_type(TypeGroup::Normal)]
+pub struct TestObjC {
+    #[tag]
+    tag: i32
+}
+
+impl TestObjC {
+    pub fn new(tag: i32) -> Self {
+        Self {tag}
+    }
+}
 
 #[derive(IObj, Debug)]
 #[obj_type(TypeGroup::Normal)]
@@ -86,6 +98,6 @@ pub fn basic_obj_store_test() {
     ite.next();
     assert!(ite.next().is_none());
 
-    assert_eq!(*st.get_tid(0).unwrap(), TypeId::of::<TestObjA>());
+    assert_eq!(*st.tid_at(0).unwrap(), TypeId::of::<TestObjA>());
 
 }

### 2024-11-14 tests/rules/mod.rs

@@ -1,7 +1,7 @@
 use meme::{core::{IObj, IRuleStat, ITaggedStore}, helpers, objs::BasicObjStore, rules::{BasicCondition, BasicEffect, BasicRuleStore}};
 use meme_derive::{IObj, IRule};
 
-use crate::objs::{TestObjA, TestObjB};
+use crate::objs::{TestObjA, TestObjB, TestObjC};
 
 #[derive(IObj, IRule, Debug)]
 pub struct TestRuleA {
@@ -19,12 +19,12 @@ impl TestRuleA {
             tag,
 
             cond: helpers::condition_builder()
-                .the_tagged(req_id)
+                .the_tagged(req_id).by_ref()
                 .build(),
 
             eff: helpers::effect_builder()
                 .crate_obj(|req| {
-                    let old = req.the_tagged(0).unwrap();
+                    let old = req.set_ref(0).unwrap();
                     let mut new_inner = 10.0;
                     if let Some(o) = old.as_any().downcast_ref::<TestObjA>() {
                         new_inner += o.get_inner()
@@ -53,14 +53,39 @@ impl TestRuleB {
 
             cond: helpers::condition_builder()
             .some_untagged::<TestObjA>(10)
-            .rand_tagged::<TestObjA>(10)
+            .rand_tagged::<TestObjA>(10).by_ref()
             .build(),
 
             eff: helpers::effect_builder()
             .crate_obj(|_| Box::new(TestObjB::new(helpers::IdGen::next_i32_id())))
             .remove_objs(|req| {
-                req.rand_tagged(0).unwrap().iter().map(|o| o.obj_tag().clone()).collect::<Vec<_>>()
+                req.rand_refs(0).unwrap().iter().map(|o| o.obj_tag().clone()).collect::<Vec<_>>()
             })
+            .build(),
+        }
+    }
+}
+
+#[derive(IObj, IRule, Debug)]
+pub struct TestRuleC {
+    #[tag]
+    t: u32,
+    #[condition]
+    cond: BasicCondition<i32>,
+    #[effect]
+    eff: BasicEffect<i32>
+}
+
+impl TestRuleC {
+    pub fn new(tag: u32) -> Self {
+        Self {
+            t: tag,
+
+            cond: helpers::condition_builder()
+            .build(),
+
+            eff: helpers::effect_builder()
[…]

### 2024-12-03 paper/src/paper.tex
完善了论文
增加了自动化脚本

增加了benchmark

微小性能优化

% Copyright 2024 Junshuang Hu
\documentclass[9pt,a4paper,twoside]{article}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{svg}
\usepackage{tabularx}
\usepackage{booktabs}

\newcommand\figpath{../assets/figures/}

\newcommand\putpic[3]{%
  \put(#1\wd0,#2\ht0){#3}%
}

\newcommand\putonsvg[2] {%
    \setbox 0 = \hbox{\includesvg{\figpath #1}}%
    \begin{picture}(\wd0, \ht0)%
        \put(0,0){\includesvg{\figpath #1}}%
        #2%
    \end{picture}%
}

\title{
    Augmented general P systems and high efficiency emulation
    \footnote{
        This work is licensed under CC BY-SA 4.0. To view a copy of this license, visit 
        https://creativecommons.org /licenses/by-sa/4.0/
    }
}

\date{2024-11-11 Draft}
\author{JunShuang Hu\footnote{llllIIIlIllIII@outlook.com}}

\begin{document}

    \maketitle
    \pagenumbering{arabic}

    \begin{abstract}
        blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah 
    \end{abstract}
    \keywords{Membrane Computing, P Systems, Emulation}

    \section{Introduction}

        Based on behaviors of organism in the cell's level, a novel kinds of computing model was formulated. Separation of areas by membranes,
        transportation of matters across membranes and biochemical reactions in membranes are the three important behaviors of cells. 
        These behaviors are captured in symbolic way to crate P systems which transform those behaviors into basic elements for general computing.

        ...

        blah

        blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah

         ...

    \section{Purpose of Research}
        Since the very first definition of P system, numerous P systems are defined, some introduced new forms of objects and rules, 
        some designed new representation of membrane. They expanded P system's application ares, enhanced P systems' computing ability.

        Nevertheless, the existing researches mostly focused on improving P systems, rather than the definition of P systems.

        This paper provided an augmented general way of define P systems with object expanding, object subdivision, rule polymorphism and cross system 
        reusing. These methods makes it easier to design and define P systems in a more concise way, especial 
        when abstracting from some complex biological behaviors.

        Design of P systems needs verification, if the designed system is too complex, step-by-step verification manually could be 
        frustrating, hence computer emulation of P system could be helpful in P system design verification.

        Some P systems are build for current applications. In the help of P system's structural advantage, like other biology inspired 
        systems, P systems implemented on modern silicon based computers could be powerful in certain application areas, thus having a emulation tool
        will reduce the time and energy of implementing these systems.

        The existing emulation tools and libraries are not high efficient or efficient but not general. 
        This paper provided a novel membrane computing library which is efficient and general for implementing the emulator for varies kind of P systems.

        blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah

         blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah

          blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah

           blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah

    \section{Augmented general P system}
        This paper provided an augmented general way of define P systems with object expanding, object subdivision, rule polymorphism and cross system 
        reusing. These methods makes it easier to design and define P systems in a more concise way, especial

        P systems defined in the augmented general way are called augmented general P systems.
        \subsection{Objects}
            Objects definition is in a more refined way in augmented general P system, such consideration is called object subdivision. We use untagged objects in
            situations that rules only care about objects of some types, and use tagged objects when individual objects matters. This is under the inspiration of 
            biochemical reactions of different types.
        \subsubsection{Tagged Objects}

            In a augmented general P system tags are used to distinguish different objects of a certain type. 
            A tagged object is defined as $o = (ty, tg)$ where $ty \in S_y, tg \in S_g$ and $S_y, S_g$ are sets of strings on alphabet $A_y, A_g$ separately. 
            $ty$ denotes the type of this object and $tg$ is the tag for this object in its type.

            e.g. chromosome $o_1 = (\text{``Human Chromosome''}, 22)$ 
            and $o_2 = (\text{``Human Chromosome''}, 1)$
            \paragraph{Uniqueness of tagged objects}

                For two objects $o_1 = (ty_1, tg_1)$ and $o_2 = (ty_2, tg_2)$, we say $o_1$ and $o_2$ are the same object if and only if 
                $ty_1 = ty_2$ and $tg_1 = tg_2$.
            \paragraph{Objects of the same type}

                For two objects $o_1 = (ty_1, tg_1)$ and $o_2 = (ty_2, tg_2)$, we say $o_1$ and $o_2$ are of the same type if and only if 
                $ty_1 = ty_2$.
            \paragraph{Unique properties of tagged objects}

                Because every tagged objects are different, there could be some unique properties for a certain object that affect how rules could be 
                applied, these properties can be used to simplify the design of rules which abstracted from behaviors like gene expression or protein functioning.

                The properties $p$ of object $o$ is defined as $p = Property(o)$, where $Property: O_t \rightarrow P$, $O_t$ is a set of tagged objects,
                $P$ is the power set of the union of sets $S_1, S_2,...,S_n$, $S_1, S_2,...,S_n$ represent different kinds of properties .

                e.g. for
                $o_1 = ($``protein''$, 1)$,
                $o_2 = ($``protein''$, 2)$,
                $Property(o_1) = \{$``has glycine''$,$``10 amino acids''$,42\}$,
                $Property(o_2) = \{$``has leucine''$,$``20 amino acids''$,233\}$

                This allows to express almost anything related to a certain object further used by rules.

        \subsubsection{Untagged Objects}

            Untagged objects are more like the original definition of objects in previous P systems.
            Untagged objects are described as a type of objects, an untagged object is defined as $u = ty$ where $ty \in S_y$ and $S_y$ is a set of strings on alphabet $A_y$.

            It is useful when designing rules for a type of objects like the rule from proteolysis in which case the differences of each protein are out of concern.
            Untagged objects ignores the difference of objects of the same type. e.g. carbohydrate $u_1 = \text{``Galactose''}$ and $u_2 = \text{``Glucose''} $
            \paragraph{Amount of untagged objects:}

                Let $Amount: O_u \rightarrow \mathbb{R}$ be the mapping of the amount of a untagged object from $O_u$.
                Let $a_{ty} = Amount_\omega(ty)$ be the amount of object of type $ty$ in region $\omega$, where $\omega \in S$ and $Amount_\omega: S_y \rightarrow \mathbb{R}$, 
                $S$ and $S_y$ are sets of strings. The following equation is always satisfied.
                \begin{equation}
                    \begin{align}
                        a_{ty} &= Amount_\omega(ty) \\
                        &= \sum_{o \in O'}{Amount(o)} \\
                    \end{align}
                \end{equation}
                where $O' = \{ o_i = ty_i \mid o_i \in O_u, o_i\text{ is in region }\omega, ty_i = ty \} $. This is equivalent to the expression with multi-set of 
                untagged objects in a region, where the multitude of each object is a real number which corresponding to the amount of objects in a region.

            \paragraph{Untagged reference of tagged object}

                Let $Amount_t: O_t \rightarrow \mathbb{R}$ be the amount of a single tagged object in $O_t$, if not defined, $Amount_t(o) = 1$.
                For tagged objects $o_1, o_2,...,o_n, n \in \mathbb{N}^+$ and $a_i = Amount_t(o_i)$, where $o_i = (ty, tg_i)$ and pair $p_i=(o_i, a_i)_{amount}$ 
                of mapping $Amount_t$ satisfies $p_i \in Property(o_i)$ for $1 \leq i \leq n$.

                Let $a = \sum{a_i}$, the untagged reference of $o_1, o_2, ..., o_n$ is $u_r = ty$ with $Amount(u_r) = a$. $o_1, o_2, ..., o_n$ are called
                the original objects of $u_r$. Note that the original objects of a untagged reference is not unique.

                Untagged objects are like small molecules while tagged objects are like macromolecules. Conditions with untagged objects usually correspond to the
                statistical characteristics of small molecules, like concentration, while tagged objects are for reactions in molecule level, like gene expressions.
                They represent real life objects in different scales, the untagged reference is a bridge between them, allows the same object to be used in different
                scale.

                Note that $Amount_t$ is not the ``amount of this tagged object'', rather, it is ``the amount the untagged object that this tagged object turned into''.
                Due to the uniqueness of tagged objects, ``the amount of this tagged object'' should always be one across all regions.

    \subsection{Rules}

        A rule $r$ is in the form of $r: c \rightarrow e_c$, $c \in C_O$ is called the condition of $r$ and $e_c \in E_c$ is called the effect of $r$ under its
        condition $c$, $C_O$ is a set of conditions on objects $O$ and $E_c$ is a set of effects under condition $c$.

        \paragraph{Tagged reference of rule}

            For a rule $r: c \rightarrow e_c$ in region $\omega$, it can be seen as a tagged object $o_r = (r, \omega)$ with $(c \rightarrow e_c) \in Property(o_r)$
            or vice versa. $o_r$ is then called the tagged reference of $r$, and $r$ is called the original rule of $o_r$. When there's no confusion, $r$ and $o_r$
            can share a same symbol.

            For clarity of expression, the variable parts of the rule's condition and effect should be written as variables along with the rule definition. Let
            $a_1, a_2,..,a_n$($n \geq 1$) be the variable of rule $r$, $r$ is defined as $r(a_1, a_2,...,a_n): c \rightarrow e_c$.
            Further, $a_i \in Property(o_r), 1 \leq i \leq n$

            Once rules are taken as objects, they can be modified by other rules, or itself, this brings more flexibility to the system. For example in a spiking neural  
            P system with dynamic threshold, each time the fire rule has been applied, the threshold of the fire rule will be changed. Therefore the condition of firing
            rule is not static, but its original definition implicitly used this concept. In augmented general P systems, this mutability must be used explicitly with
            tagged references for a clear and unified expression.

        \subsubsection{Conditions}

            Let $C_u = \{(u, a) \mid u \in O_u \cup O_{ru}, a \in \mathbb{R}\}$ where $O_u$ is a set of untagged objects and $O_{ru}$ is a set untagged references.
            Let $C_t = O_t \cup O_{rt}$ where $O_t$ is a set of tagged objects and $O_{rt}$ is a set tagged references.
            The set of conditions on $O = O_t \cup O_u$ is $C = \{(c_t, c_u) \mid c_t \subseteq C_t, c_u \subseteq C_u\}$ 
            where $O_t$ is a set of tagged objects and tagged references.

            \paragraph{Determined condition and non-determined condition}
                Condition $c=(c_t, c_u)$ is a determined condition if and only if there is no untagged references in
                $c_u$, else it is a non-determined condition.

                A rule with non-determined condition requires the region to have a certain amount of tagged objects of some types, 
                but the exact objects used for this rule is chosen in a non-determined way.

                e.g. 
                $c_1 = (\{o_{t1}, o_{t2}\}, \{(u_1, 10.0), (u_2, 5.0)\})$ for tagged objects $o_{t1}, o_{t2}$ and untagged objects $u_1, u_2$,
                or more realistically
                $c = (\{ o_1=($``protein''$,$ $1)$ $,$ $ o_2=($``protein''$,$$ 2) \}$ $,$ $ \{(u_1=$``temperature'' $,$
                $40)$ $,$ $ (u_2=$``pH''$,$$ 8.1)\})$.

        \subsubsection{Effects}

            The set of all effect under condition $c=(c_t, c_u)$ is $E_c = \{ f_c \mid f_c: P(O_c) \rightarrow P(I) \}$  where $P(O_c)$ is the power set of 
            $O_c$, $O_c = \{o \mid o \in c_t \vee o \in c_u\}$. $P(I)$ is a power set of influences $I$.

            Influences describe how a region acts under an effect, for the sack of generality, they are not strictly defined. 
            Depends on the type of the membrane that defines the region, influences may be interpreted differently, this feature is called rule polymorphism.

            Across all membranes, the following types of influences are always recognizable, namely, they are universal influences.
            \paragraph{Universal influences}
                A universal influence $i \in I_U$ is defined as $i = (op, (o,a))$, where $op \in \{\text{``Add''}$ $,$ $ \text{``Remove''}, \text{``Stop''}\}$$,$$ o \in O_t \cup O_u \cup \{\epsilon\}$,
                $a \in \mathbb{R} \cup \{\epsilon\}$ is the amount of the object to be removed, $O_t$ is a set of tagged objects, and $O_u$ is a set of untagged objects, 
                $\epsilon$ denotes no object or amount is required.

                If $a = \epsilon$ then $i$ can be written as $i = (op, o)$, if $a = \epsilon$ and $o =\epsilon$,  $i$
                can be written as $i=op$. 
                \begin{itemize}
                    \item ``Add'' insists the object $o$ to be added to the region $\omega$ where the rule is applied. 
                        If $a \neq \epsilon$, 
                            when $o$ is tagged, $Amount_t(o) = a$ is added to $Property(o)$, 
                            when $o$ is untagged, $Amount_\omega(o) = a$ is added to region $\omega$.

                        If $o$ already exists in $\omega$,
                            when $o$ is tagged, the existing object is replaced, for convenience, changes of properties of $o$ can be marked after
                            its symbol as $o(p_1 = p_1', p_2 = p_2',..., p_n = p_n')$
                            when $o$ is untagged, $a_{old} = Amount_\omega(o)$ is replaces by $a_{new} = a_{old} + a$.

                        For untagged object, $a$ can not be $\epsilon$.

                    \item ``Remove'' insists the object $o$ to be removed in the region where the rule is applied, $o$ must be in the condition of the rule, $a$ is ignored.

                    \item ``Stop'' insists the region where the rule is applied to stop evolving, $o$ must be $\epsilon$.
                \end{itemize}

                e.g. for rule $r: c \rightarrow e_c$, $c = (\{ o_1=(\text{``protein''}, \text{'a'}) \}, \{(u_1=\text{``enzyme''}, 10)\})$, 
                $e_c = \{ (\{o_1\}, \{(\text{``Remove''}, o_1)\})\} $

                An effect for a rule is a mapping over a subset of objects in the rule's condition to a set of influences.

            \paragraph{Multi-Branch Effects and Single Branch Effects}
            A multi-branch effect $e_c$ has a set of sets of influences ${is_1, is_2, ..., is_n}$, only one set of influences is applied each time, the set chosen is determined when $e_c$ is calculated. If only one set of influences exists, the effect is a single branch effect.

            \paragraph{Satisfaction of rules and applying rules}

                For a rule $r: c \rightarrow e_c$ in region $\omega$, $c = (c_t, c_u)$, we call this rule is satisfied in $\omega$ if and only if 
                $\forall o_t \in c_t$ $,$ $ \forall (o_u, a_u) \in c_u$ $,$ $o_t \in O_{\omega}, o_u \in O_{\omega} \text{ and } Amount_\omega(o_u) \geq a_u$.

                If rule $r$ is satisfied in region $\omega$, then to apply $r$ in $\omega$ is to calculate the effect mapping $e_c$ to get influences $i$,
                and region $r$ uses $i$ to update itself.

                If the condition of a rule is empty, then the rule is always satisfied. If the effect of a rule is empty, then the rule produces no influence.

        \subsubsection{Simplified rule notations}

            For rule $r(a_1,a_2,...a_n): c \rightarrow e_c$, where $c=(c_t, c_u)$, the simplified rule expression is:
            \begin{equation}
                \begin{align}
                    &r(a_1,a_2,...a_n): \\
                    &c_1 \rightarrow e_c(c_1)  \\
                    &c_2 \rightarrow e_c(c_2)  \\
                    &...\\
                    &c_n \rightarrow e_c(c_n)  \\
                \end{align}
            \end{equation}
            or in a single line
            \begin{equation}
                r(a_1,a_2,...a_n): c_1c_2...c_n \rightarrow e_c(c_1)e_c(c_2)...e_c(c_n)
            \end{equation}
            where
            \begin{equation}
                \bigcup_{k = 1}^{n}{c_k} = c_t \cup c_u, \bigcap_{k = 1}^{n}{c_k} = \emptyset
            \end{equation}

            Then, $c_k = \{o_{k1},o_{k2},...,o_{kp}\} \cup \{(u_{k1},a_{k1}), (u_{k2},a_{k2}),..., (u_{kq},a_{kq})\}$ for $1 \leq k \leq n$ can be written as 
            $o_{k1}o_{k2}...o_{kp}(u_{k1}, a_{k1})(u_{k2}, a_{k2})...(u_{kq}, a_{kq})$.

            The properties $p_1,p_2,...,p_l$ of object $o$ can be written in parentheses after the object symbol in both condition and effect as $o(p_1,p_2,...,p_l)$ if needed.

            In all notations, if symbol '$,$' is not included in the alphabet of object or rule names, then it can be used to separate object or rules names, e.g. $o_1,o_2,o_3$ and $r_1,r_2,r_3$.

            Symbol $\epsilon$ is used to denote no condition or effect required.

            \paragraph{When using universal influences}
            If $i_k = e_c(c_k)$ are universal influences $\{ (op_1,$ $ (o_1,a_1)),$ $ (op_2, (o_2,a_2))$ $,...,$ $(op_m, (o_m,a_m))  \}$, 
            $i_k$ can be written as $op_1$ $(o_1, a_1)$ $op_2$ $(o_2, a_2)...$ $op_m(o_m, a_m)$, or in the following way:
            \begin{itemize}
                \item If $op_i$ is Add$(o)$, write as $o$.
                \item If $op_i$ is Remove$(o)$, write nothing.
                \item For any object $o$ in the condition $c_k$, if Remove$(o) \notin i_k$, write as $o$.
                \item If there are two untagged objects $(ty_1, a_1)$ and $(ty_2, a_2)$ in the simplified effect with $ty_1 = ty_2$, write as $(ty_1, a_1 + a_2)$.
            \end{itemize}

            \paragraph{When using property matching effect with two branches}
             For a rule $r: c \rightarrow e_c$, $c=c_t \cup c_u$, if $e_c$ is a multi-branch effect in the following form:
            \begin{equation}
                e_c=\left\{
                \begin{align}
                    & i, \forall o_i \in c_t, p_i \subseteq Property(o_i)\\
                    & \epsilon, otherwise
                \end{align}
                \right
            \end{equation}
            where $p_i$ and $1 \leq i \leq n$ is the properties required by effect to take place, then the rule can be simply written as
            \begin{equation}
                 r: c_uo_1(p_1)o_2(p_2)...o_n(p_n) \rightarrow i
            \end{equation}

            e.g. 
            \begin{equation}
                \begin{align}
                    &r_1: \\
                    &o_1o_2(u_1, 10) \rightarrow \text{Remove}(o_1)\text{Add}(u_1, 5)  \\
                    &o_3 \rightarrow \text{Add}(o_5) \\
                    &o_4 \rightarrow \text{Remove}(o_4)\text{Add}(o_4(some,new,props)) \\
                    &(u_2, 20) \rightarrow \epsilon \\
                \end{align}
            \end{equation}
            or
             \begin{equation}
                \begin{align}
                    &r_1: \\
                    &o_1o_2(u_1, 10) \rightarrow o_2(u_1, 15)  \\
                    &o_3 \rightarrow o_3o_5 \\
                    &o_4(with,old,props) \rightarrow o_4(some,new,props) \\
                    &(u_2, 20) \rightarrow (u_2, 20) \\
                \end{align}
            \end{equation}
            or
            \begin{equation}
                \begin{align}
                    &r_2(a): \\
                    &(u_1, a) \rightarrow \text{Remove}(u_1) \\
                    &r_2(a_{old}) \rightarrow \text{Add}(r_2(a = a_{old} + 1))
                \end{align}
            \end{equation}
            or
            \begin{equation}
                \begin{align}
                    r_3: o_1,o_2,(u_1, 60) \rightarrow \text{Add}(o_3)\text{Remove}(o_2)
                \end{align}
            \end{equation}
            or
            \begin{equation}
                \begin{align}
                    r_4:\epsilon \rightarrow \text{Add}(o_1)\text{Add}(u_1, 1.1)
                \end{align}
            \end{equation}

        \subsection{Membranes}

            In augmented general P systems, a membrane $m$ is defined as $m=(\omega, O_s, R_s, F)$ where $F = (Check^*, Apply^*, Deref_u^*, Deref_t^*, Evolve)$ is the feature tuple of $m$ (or feature for short), $\omega$ is the region defined by $m$, $O_s$ and $R_s$ are objects and rules in $m$.
            Let $O = O_t \cup O_u \cup O_{rt} \cup O_{ru}$ be the set of all possible objects, let $R$ be the set of all possible rules and let $I$ be the set
            of all recognizable influences.

            \paragraph{Difference between membrane and region}
            Region $\omega$ is an area that surrounded by a membrane, everything in the area including sub-regions are inside of the region, while membrane of region $\omega$, or simply membrane $\omega$, only refers to the features, objects and rules of the region excluding its sub-regions.
            \paragraph*{}

            Different types of membranes may have different behaviors or strategies and corresponding to the different feature tuples. Feature tuple decides how a region under a specific membrane should evolve, 
            behaviors of a membrane is abstracted into the following mappings.

            \begin{itemize}
                \item  $Check: (R, P(O)) \rightarrow \{yes, no\}$ is a mapping a rule and a set of objects to a result of $yes$ or $no$, representing the
                the membrane's logic of decide whether a rule can be applied or not on a set of existing objects in a region.

                \item  $Apply: (I, P(O)) \rightarrow P(O)$ is a mapping from an influence and a set of objects to a set of updated objects,
                it represents the rule's logic on handling an influence on a set of objects.

                \item $Deref_u: (O_{ru}, \mathbb{R}) \rightarrow P(O_t)$ represents the logic of the membrane on decide the original objects of a untagged reference
                of a certain amount.

                \item $Deref_t: O_{rt} \rightarrow R$, represents the logic of the membrane on decide the original rule of a tagged reference.

                \item $Evolve: (P(O), P(R)) \rightarrow (P(O), P(R))$ defines how this membrane is evolving in each iteration.

            \end{itemize}

                For a feature tuple, only $Evolve$ mapping is required, other mappings are optional and marked with ``$*$''.
                When processing influences, the following two actions can be done automatically.

            \begin{itemize}
                \item Before the effect calculation, if an object is a untagged reference, it will be mapped into tagged objects with $Deref_u$ with the same amount.
                \item After $Apply$ mapping, if an object is a tagged reference, it will be mapped into a rule with $Deref_t$, and the corresponding rule is added or removed. 
            \end{itemize}

            Note that in a augmented general P system, there could be different kinds of membranes existing and collaborating in the same time, to let a P system that use other P systems as subsystems to be defined. Cross system reusing is used to achieve this.

            \paragraph{Single P systems and Composite P systems}
            A P system with one type of membrane (i.e. one feature set) or no membrane is a single P system, otherwise it is a composite P systems. A composite P system can be seen as a combination of many single P systems which are called its subsystems.

            \subsubsection{Default scheme of $Evolve$}
                Mapping $Evolve$ can be defined in any form depending on the requirement of the specific system. Default scheme of $Evolve$ gives an optional default structure for systems that build upon augmented general P system, as showing in table 1.
                \begin{table}[!htbp]
                    \centering
                    \begin{tabularx}{\textwidth}{lX}
                        \toprule
                        Step & Actions \\ 
                        \midrule
                        0    & Let input be $O_s$ and $R_s$.\\
                        1    & For every rule $r\in R_s$, get the set of all satisfied rules $R_a=\{r \mid Check(r, O_s) = yes \}$, where $O_s = O_{st} \cup O_{su}$ \\
                        2    & For each $r: c \rightarrow e_c, r \in R_a$, use the simple deadlock avoid algorithm in Table 2 to get the parallel satisfied rule set $R_{ap}$.\\
                        3    & For all untagged references and amount $(o_{ru}, a)$ in the conditions of rule $r$ in $R_{ap}$, let $O_{du,r} = Deref_u(o_{ru}, a)$.\\
                        4    & Apply each rule $r$ in $R_{ap}$ in parallel to get the set of influences $I_r$.\\
                        5    & Crate a empty set of objects $O_p = O_{pt} \cup O_{pu}$.\\
                        6    & Let set $O_d = O_t \cup O_u$ , where $O_t = O_{st} - O_{pt}$ and $O_u = \{(ty,a)\mid a = a' - a'' $ for $ (ty, a') \in O_{su} $ and $ (ty, a'') in O_{pu} \}$.\\
                        7    & For every rule $r_d, r_d \in R_a \vee r\notin R_{ap}$, if $Check(r, O_d) = yes$, get $O_{du,r_d}$ as in Step 3 and add get its influences $I_{r_d}$, then add objects in its condition to $O_p$.\\
                        8    & Repeat Step 6 and Step 7 until all rules are tested.\\
                        9    & For $I_r$ of rule $r$, for each $i \in I_r$ let $O_n = Apply(i, O_s \cup O_r \cup O_{du,r})$, where $O_r$ is the set of tagged references on $R_s$.\\
                        10   & Let $O_n = O_{no} \cup O_{nr}$ where $O_{no}=\{ o \mid o \text{ is not a reference }\}$ and $O_{nr}=\{ o \mid o \text{ is a reference }\}$. Get $R_n=\{r \mid r = Deref_t(o), o \in O_{nr}\}$, then let $O_s = O_{no}$ and $R_s = R_n$.\\
                        11   & Repeat Step 9 and Step 10 until all influences are processed. The Updated $O_s$ and $R_s$ are output.\\
                        \bottomrule
                    \end{tabularx}
                    \caption{Default $Evolve$ mapping}
                    \label{tab:evolve}
                \end{table}

                \begin{table}[!htbp]
                    \centering
                    \begin{tabularx}{\textwidth}{lX}
                        \toprule
                        Step & Actions \\ 
                        \midrule
                        1    &  Build a request matrix from the condition of rules in $R_a$ with each requested count is amount for untagged object and one for tagged object.\\
                        2    &  maintain a resource matrix which is sync to the objects in the region.\\
                        3    &  compare request matrix with the resource matrix, find all rules that does not need objects more than the existed. \\
                        \bottomrule
                    \end{tabularx}
                    \caption{Simple deadlock avoid algorithm}
                    \label{tab:deadlock}
                \end{table}

            \subsubsection{Simplified region notations}
                A region $\omega$ defined by membrane $m=(\omega, O_s, R_s, F)$ can be written as the 
                following string representation if needed.
                \begin{equation}
                    \omega: [ o_1o_2...o_n \mid r_1r_2...r_m \mid Sub_1Sub_2...Sub_k ]_F
                \end{equation}
                where $O_s = \{ o_1, o_2,...,o_n \}$ and $R_s = \{r_1,r_2,...,r_m\}$, ``$[$ $]_F$'' represents the membrane that defines this region with feature $F$, $Sub_i$,$0 \leq i \leq k$ is regions inside of $\omega$, defined recursively. $n,m,k \in \mathbb{N}$. Regions also have a graph representation, as in figure 1.
                \begin{figure}[!htbp]
                    \centering
                    \putonsvg{region.svg}{
                        \putpic{.2}{.6}{\Large$o_1o_2...o_n$}
                        \putpic{.2}{.4}{\Large$r_1r_2...r_m$}
                        \putpic{.7}{.82}{\large$Sub_1$}
                        \putpic{.7}{.54}{\large$Sub_2$}
                        \putpic{.7}{.15}{\large$Sub_k$}
                        \putpic{.1}{.1}{\Large$F$}
                        \putpic{.1}{.9}{\Large$\omega$}
                    }
                    \caption{Graph representation of a region}
                    \label{fig:fig1}
                \end{figure}

        \subsection{Cross system reusing}
            Typically, a P system can be defined with only one type of membrane, different membranes of the same type are relatively easy to collaborate since they shared the same definition.

            A composite augmented general P system includes different kinds of membranes, these membranes are different in their features. When these membranes are collaborating and evolving together, a set of principles must be followed for them to share information, i.e. objects.

            Augmented general P system uses a concept called cross system reusing to deal with the collaboration of different types of membranes.

            For two single P system $P_1$ and $P_2$, $O_1$ is a set of all possible objects in $P_1$, and $O_2$ is a set of all possible objects in $P_2$, $O_c = O_1 \cap O_2$ is called the cross system objects on $P_1$ and $P_2$. A rule $r: c \rightarrow e_c$, $r$ is a cross system rule on $P_1$ and $P_2$ if and only if $c \subseteq O_c$ and $I = dom(e_c)$ is a set of universal influences.

            Aside from the collaboration of different types of membranes, cross system objects and rules can be used for the definition of novel P systems with objects and rules that wildly exists. In biological cells, some reactions can take place in almost every cell, one typical example is the hydrolysis of adenosine triphosphate (ATP), rules and corresponding objects can be designed for membranes that utilize this reaction.

        \subsubsection{Cross system communication}
            With cross system reusing, augmented general P system employments a way of sending objects across different types of membranes without relay on the features of membranes.

            Cross system communication is based on the following objects and rules:
            \begin{itemize}
                \item Channel Objects: channel objects $ch_a, ch_b$ are paired objects representing a bidirectional channel of any form. When in a same region, carrier Objects can enter $ch_a$, and been transported to the region where $ch_b$ belongs to, or vice versa.
                \item Carrier Objects: carrier Objects are objects that can carry objects withing their property and been transported from one side of the channel to the other. Property of a carrier object $ca$ is in the form of $Property(ca)=\{ ch, o\}$, where $ch$ is the channel object that this carrier will enter and $o$ is the object it carries.
                \item Send Rule: a send rule is $r_s: ch_1ch_2...ch_nca \rightarrow e_s$, $ch_1ch_2...ch_n$ are its known channels, this rule will send a carrier to its corresponding channel and remove the carrier from current region. $e_s = $Remove$(ca)$ when object is sent, otherwise $e_s=\epsilon$. 
                \item Receive Rule: a receive rule is $r_r: ch_1ch_2...ch_n \rightarrow e_r$, this rule will take one object out from the channels. $e_r = $Add$(ca)$ when there is object in the channels, otherwise $e_r=\epsilon$. 
            \end{itemize}

            e.g. for two region $1:[o,ch_a \mid r_0,r_s]_{F_1}$ and $2:[ ch_b \mid r_1,r_r]_{F_2}$
            where
            \begin{equation}
                \begin{align}
                    &r_0: o \rightarrow ca(o,ch_a) \\
                    &r_s: ch_a,ca(o,ch_a) \rightarrow ch_a \\
                \end{align}
            \end{equation}
            and 
            \begin{equation}
             \begin{align}
                    &r_1: ca(o) \rightarrow o \\
                    &r_r: ch_b(ca) \rightarrow ch_b,ca\\
                \end{align}
            \end{equation}

            Cross system communication can also be used to integrate any P system to a augmented general P system.

            By default, when there is a channel object in the region, the corresponding send and receive rules are added and can be ignored from the string or graph notations of the region, since for every system, send rules and receive rules are identical except their known channels and the know channels are all channels available in the region.

            \paragraph{Graph representation of cross system communication}
            Membranes of region $\omega_1:[o_1o_2$ $...o_n,$ $ ch_a \mid $ $r_1r_2...r_m,$ $ r_s,r_r]_{F_1}$ and $\omega_2:[o_1'o_2'...o_j',$ $ ch_b \mid$ $ r_1'r_2'...r_k',$ $ r_s,r_r]_{F_2}$ can be represented with a graph representation as in Figure 2, the two-way arrow indicates that both region have send and receive rules, when one region only has a send rule and the other only has a receive rule, use a one-way arrow.
            \begin{figure}[!htbp]
                \centering
                \putonsvg{region_com.svg}{
                    \putpic{.1}{.6}{$o_1o_2...o_n$}
                    \putpic{.75}{.6}{$o_1'o_2'...o_j'$}
                    \putpic{.1}{.4}{$r_1r_2...r_m$}
                    \putpic{.75}{.4}{$r_1'r_2'...r_k'$}
                    \putpic{.025}{.1}{$F_1$}
                    \putpic{.625}{.1}{$F_2$}
                    \putpic{.025}{.85}{$\omega_1$}
                    \putpic{.625}{.85}{$\omega_2$}
                    \putpic{.325}{.5}{$ch_a$}
                    \putpic{.625}{.5}{$ch_b$}
                }
                \caption{Graph representation of cross system communication between two regions}
                \label{fig:fig2}
            \end{figure}

            If the membrane of region $\omega_1$ is the immediate outer membrane of region $\omega_2$, the representation of cross system communication between them is shown in Figure 3.

             \begin{figure}[!htbp]
                \centering
                \putonsvg{region_com_2.svg}{
                    \putpic{.1}{.6}{$o_1o_2...o_n$}
                    \putpic{.7}{.6}{$o_1'o_2'...o_j'$}
                    \putpic{.1}{.4}{$r_1r_2...r_m$}
                    \putpic{.7}{.4}{$r_1'r_2'...r_k'$}
                    \putpic{.025}{.1}{$F_1$}
                    \putpic{.45}{.2}{$F_2$}
                    \putpic{.025}{.85}{$\omega_1$}
                    \putpic{.45}{.75}{$\omega_2$}
                    \putpic{.32}{.5}{$ch_a$}
                    \putpic{.5}{.5}{$ch_b$}
                }
                \caption{Graph representation of cross system communication between two regions with inclusive relationship}
                \label{fig:fig3}
            \end{figure}

    \section{High efficiency emulation for augmented general P system}

    For the requirement of fast and general emulation for P systems, a emulation library Membrane Emulation Lib (MEME for short) is designed and implemented based on the augmented general P system framework.

    The current emulation tools take a approach of using a intermediate language, like p-lingua, to describe a P system and compile it into a emulation program, or use it as interpreted language to drive the emulator.

    This brings convince for the emulation of the P systems that the intermediate language supports, but when facing a P system that the intermediate language cannot describe, the intermediate language along with its compiler and emulator or the emulation library need to be expanded to adapt the novel system, because the language level of the intermediate language is not high enough.

    The structure of the augmented general P system gives a benefit of using mappings to describe the feature of each P systems, these mappings can be implemented directly with modern program languages. Hence, not like the current emulation tools, MEME dose not requires a intermediate language to describe a P system, all code is written with program language, therefore MEME can be used to implement more P systems without the update to the library itself.

    Another main benefit of MEME is its efficiency. With compiled language Rust and multi-thread design, MEME delivers a more efficient program, the implemented P system can be compiled into executable on various platforms.

    \subsection{Structure of MEME}
    MEME is designed to be a modular library, interfaces between modules and default modules are provided. Modules of MEME can be combined with custom modules to expand the function of MEME or to optimize the performance.

        \subsubsection{Top level interfaces}
        Objects, rules and membranes are three most important things of a P system. Every object, rule or membrane in MEME must implement the corresponding interface IObj, IRule and IMem. Interfaces IObjStore and IObjStat are used for the storage and the statistic of objects in the membrane. Similarly, interface IRuleStore and IRuleStat are used for the storage and the statistic of rules in the membrane. These interfaces are the top level interfaces of MEME, their relationship is shown in Figure 4.
        \begin{figure}[!htbp]
            \centering
            \includesvg[width=\textwidth]{\figpath interface_relation.svg}
            \caption{Top level interfaces relations of MEME}
            \label{fig:fig4}
        \end{figure}

        \subsubsection{System architecture}
        The architecture diagram of MEME is shown in Figure 5.
        \begin{figure}[!htbp]
            \centering
            \includesvg{\figpath placeholder.svg}
            \caption{Architecture diagram of MEME}
            \label{fig:fig5}
        \end{figure}

    \subsection{Versatility of MEME}
    To use MEME, a P system $sys$ must satisfy the following requirements:
    \begin{itemize}
        \item $sys$ is defined or has a equivalent definition as a augmented general P system.
        \item The feature and effect mappings of $sys$ can be implemented with high-level programming language.
    \end{itemize}

    To use MEME without any custom module, a P system $sys$ must further satisfy the following requirements:
     \begin{itemize}
        \item Influences of $sys$ are all universal influences.
        \item Membranes of $sys$ evolve under default scheme.
        \item Properties of any object can be send across thread boundaries.
    \end{itemize}

    \subsection{Performance measurements}

    Indexes: CPU Usage, Memory Usage, R-HTOPS(Rules in region with one Hundred Thousand Objects Per Second)

    TR-MOPS is used to measure the performance for a single membrane.

    Rule for R-HTOPS: 
    \begin{itemize}
        \item $r_1: (o_r, 100) \rightarrow$ Add$(o_{stop})$Add$(o(ty, rtg))$Remove$(o_r, 1)$, $O$ is an untagged reference for $o$, $rtg$ is a random tag.
        \item $r_2: \epsilon \rightarrow$ Add$(send(o(ty, rtg), env))$, $env$ is the environment region, $send$ is cross system communication object.
        \item $r_{stop} (o_{stop}, 500) \rightarrow$ Stop. 
        \item $r_{com}$ is cross system communication rule.
    \end{itemize}

    $R-HTOPS = 2000 / T_{elapsed}$, where $T_{elapsed}$ is the time from system start to stop in seconds.

    Similarly, R-MOPS, R-x-HTOPS,  R-TOPS, R-x-TOPS is defined, for x hundreds thousand of objects and x thousand of objects.

    \begin{itemize}
        \item R-MOPS: 49.0461,
        \item R-5-HTOPS: 102.9548, 
        \item R-HTOPS: 1102.5358,
        \item R-10-TOPS: 10928.9617,
        \item R-TOPS: 51282.0513.
    \end{itemize}

    Platform: AMD Ryzen 5 3400G @3.7 GHz, one physical thread is used.

    R-TMPS, R-x-TMPS, R-HTMPS, R-x-HTMPS, R-MMPS

    \section{Other elements}

\end{document}

### 2024-12-03 benches/measurements.rs

@@ -1,0 +1,62 @@
+// Copyright 2024 Junshuang Hu
+use std::time::{Duration, Instant};
+
+use criterion::{measurement::{Measurement, ValueFormatter},Throughput};
+
+pub struct RxxOPS;
+impl Measurement for RxxOPS {
+    type Intermediate = Instant;
+    type Value = Duration;
+
+    fn start(&self) -> Self::Intermediate {
+        Instant::now()
+    }
+    fn end(&self, i: Self::Intermediate) -> Self::Value {
+        i.elapsed()
+    }
+    fn add(&self, v1: &Self::Value, v2: &Self::Value) -> Self::Value {
+        *v1 + *v2
+    }
+    fn zero(&self) -> Self::Value {
+        Duration::from_millis(0)
+    }
+    fn to_f64(&self, val: &Self::Value) -> f64 {
+        val.as_millis() as f64
+    }
+    fn formatter(&self) -> &dyn ValueFormatter {
+        &RxxOPSFormatter
+    }
+}
+
+pub struct RxxOPSFormatter;
+impl ValueFormatter for RxxOPSFormatter {
+    fn scale_values(&self, _: f64, _: &mut [f64]) -> &'static str {
+       "μs"
+    }
+
+    fn scale_throughputs(
+        &self,
+        _: f64,
+        throughput: &Throughput,
+        values: &mut [f64],
+    ) -> &'static str {
+        match *throughput {
+            Throughput::Bytes(_) =>{
+                "Unsupported"
+            },
+            Throughput::BytesDecimal(_) => {
+                "Unsupported"
+            }
+            Throughput::Elements(elems) => {
+                for v in values {
+                    *v =  elems as f64 * 4_000.0 / *v;
+                }
+                "rules/sec"
+            },
+        }
+    }
+
+    fn scale_for_machines(&self, _: &mut [f64]) -> &'static str {
+        "μs"
+    }
+}

### 2024-12-03 benches/meme_benchmark.rs

@@ -1,0 +1,186 @@
+// Copyright 2024 Junshuang Hu
+mod measurements;
+
+use criterion::{criterion_group, criterion_main, BatchSize, Criterion, Throughput};
+//use pprof::criterion::{Output, PProfProfiler};
+
+use measurements::RxxOPS;
+use std::{thread, time::Duration};
+
+use meme::{
+    core::{
+        IMem, PObj, RequestedObj,
+    }, helpers, mems::basic::BasicMem, objs::com::{ObjChannel, SendMsg, SendWrapper}, rules::{
+        com::SendReceiveRule, BasicCondition, BasicEffect
+    }
+};
+use meme::meme_derive::{IObj, IRule};
+
+#[derive(IObj, IRule, Debug)]
+pub struct BenchRuleAct {
+    #[tag]
+    t: u32,
+    #[condition]
+    cond: BasicCondition<u32>,
+    #[effect]
+    eff: BasicEffect<u32>
+}
+
+impl BenchRuleAct {
+    pub fn new(tag: u32, rtgd_amount: usize) -> Self {
+        Self {
+            t: tag,
+
+            cond: helpers::condition_builder()
+            .rand_tagged::<BenchO>(rtgd_amount).by_tag()
+            .build(),
+
+            eff: helpers::effect_builder()
+            .remove_obj(|req: &mut RequestedObj<u32>| {
+                req.rand_tags(0).unwrap().get(0).unwrap().clone()
+            })
+            .crate_obj(|_| Box::new(BenchO::new(helpers::IdGen::next_u32_id())))
+            //.crate_obj(|_| Box::new(StopObj { tag: helpers::IdGen::next_u32_id() }))
+            .increase_untagged::<StopObj>(1)
+            .build(),
+        }
+    }
+}
+
+#[derive(IObj, Debug)]
+pub struct StopObj {
+    #[tag]
+    tag: u32
+}
+
+#[derive(IObj, IRule, Debug, Clone)]
+pub struct BenchStopRule {
+    #[tag]
+    tag: u32,
+    #[effect]
+    eff: BasicEffect<u32>,
+    #[condition]
+    cond: BasicCondition<u32>
+}
+
+impl BenchStopRule {
+    pub fn new(tag: u32, stop_amount: u32) -> Self {
+        Self {
+            tag,
+
+            cond: helpers::condition_builder()
+                .some_untagged::<StopObj>(stop_amount)
+                .build(),
+
[…]

### 2024-12-03 src/core.rs

@@ -107,6 +107,10 @@ pub trait IObjStat<Unit: Scalar> {
     fn amount_of(&self, ty: &ObjType) -> Option<Unit>;
     fn amount_of_many(&self, tys: &[ObjType]) -> Vec<&Unit>;
 
+    fn amounts_u(&self) -> impl Iterator<Item = &Unit>;
+    fn amount_of_u(&self, ty: &ObjType) -> Option<Unit>;
+    fn amount_of_many_u(&self, tys: &[ObjType]) -> Vec<&Unit>;
+
     // /// 该方法用于表示是否存在对象的更改  
     // /// 如果对象被更改（或可能更改）则返回 true，否之返回 false  
     // /// 使用 [`IObjStat::dismiss()`] 来确认已处理更改，使该方法返回 false
@@ -142,9 +146,10 @@ pub trait IRuleEffect {
 /// 规则执行，这些对象能且仅能被执行的规则修改  
 /// 只记录 Untagged 的需求量，tagged 对象需要即时计算  
 pub trait ICondition<Tag: Clone + Hash + Eq, Unit: Scalar>: Clone {
-    fn from_builder(uts: Option<UntaggedPresences<Unit>>, tgs: Option<TaggedPresences<Tag>>) -> Self;
+    fn from_builder(uts: Option<UntaggedPresences<Unit>>, tgs: Option<TaggedPresences<Tag>>, skip_take: bool) -> Self;
     fn untagged(&self) -> &Option<UntaggedPresences<Unit>>;
     fn tagged(&self) -> &Option<TaggedPresences<Tag>>;
+    fn skip_take(&self) -> bool;
 }
 
 
@@ -246,7 +251,8 @@ where OT: Clone + Hash + Eq, U: Scalar, C: ICondition<OT, U> {
                     let einfo = ExecutableInfo { 
                         rule_index: i, 
                         rand_tags: choosed_each,
-                        requested_tag: RequestTyped::new_opt(tag_set, tag_rand)
+                        requested_tag: RequestTyped::new_opt(tag_set, tag_rand),
+                        skip_take: c.skip_take()
                     };
                     let mut tag_confli = false;
                     if c.tagged().is_some() {
@@ -392,7 +398,8 @@ where OT: Clone + Hash + Eq, U: Scalar, C: ICondition<OT, U> {
                     let einfo = ExecutableInfo { 
                         rule_index: i, 
                         rand_tags: choosed_each,
[…]

### 2024-12-03 src/helpers.rs

@@ -62,6 +62,18 @@ where T: Send + Sync, U: Send + Sync {
         self
     }
 
+    pub fn increase_untagged<O: IObj +'static>(mut self, amount: U) -> Self {
+        let e = self.effs.get_or_insert(Vec::new());
+        e.push(OperationEffect::IncreaseObjUntagged((ObjType::default_group::<O>(), amount)));
+        self
+    }
+
+    pub fn decrease_untagged<O: IObj +'static>(mut self, amount: U) -> Self {
+        let e = self.effs.get_or_insert(Vec::new());
+        e.push(OperationEffect::DecreaseObjUntagged((ObjType::default_group::<O>(), amount)));
+        self
+    }
+
     pub fn stop_mem(mut self) -> Self {
         let e = self.effs.get_or_insert(Vec::new());
         e.push(OperationEffect::Stop);
@@ -81,7 +93,8 @@ pub struct ConditionBuilder<T = u32, U = u32>
 where T: Clone + Hash + Eq, U: Scalar{
     of_type: Option<UntaggedPresences<U>>,
     of_tag: Option<TaggedPresences<T>>,
-    last_added_is_otg: bool
+    last_added_is_otg: bool,
+    skip_take: bool
 }
 
 impl<T: Clone + Hash + Eq, U: Scalar> Default for ConditionBuilder<T, U> {
@@ -95,14 +108,15 @@ impl<T: Clone + Hash + Eq, U: Scalar> ConditionBuilder<T, U> {
         Self {
             of_type: None,
             of_tag: None,
-            last_added_is_otg: false
+            last_added_is_otg: false,
+            skip_take: true
         }
     }
     
     pub fn some_untagged<Obj: IObj + ?Sized + 'static>(mut self, amount: U) -> Self {
         let oty = self.of_type.get_or_insert(Vec::new());
         oty.push(UntaggedPresence {
-            ty: ObjType::new::<Obj>(&crate::core::DEFAULT_GROUP),
+            ty: ObjType::default_group::<Obj>(),
             amount,
             take: false
         });
@@ -150,7 +164,7 @@ impl<T: Clone + Hash + Eq, U: Scalar> ConditionBuilder<T, U> {
     /// ```
     pub fn rand_tagged<Obj: IObj + 'static>(mut self, count: usize) -> Self {
[…]

### 2024-12-03 src/mems.rs

@@ -2,3 +2,7 @@
 pub mod basic;
 
 // todo： 膜管理器
+
+pub struct CPUEnvRegion {
+    
+}

### 2024-12-03 src/mems/basic.rs

@@ -8,6 +8,7 @@ use crate::meme_derive::*;
 use crate::objs::BasicObjStore;
 use crate::rules::BasicRuleStore;
 
+use std::any::TypeId;
 use std::fmt::Debug;
 use std::hash::Hash;
 use std::sync::Arc;
@@ -21,6 +22,25 @@ use rand::thread_rng;
 use rayon::prelude::*;
 
 pub type PBasicRule<RT, OT, U> = PRule<RT, OT, U, U, BasicEffect<OT, U>, BasicCondition<OT, U>>;
+
+#[derive(Debug, Default)]
+pub struct EPOut<T,U> {
+    pub to_add: Vec<PObj<T,U>>,
+    pub to_remove: Vec<T>,
+    pub to_inc: Vec<(TypeId, U)>,
+    pub to_dec: Vec<(TypeId, U)>
+}
+
+impl<T, U> EPOut<T, U> {
+    pub fn new() -> Self {
+        Self { to_add: Vec::new(), to_remove: Vec::new(), to_inc: Vec::new(), to_dec: Vec::new() }
+    }
+
+    pub fn is_empty(&self) -> bool {
+        self.to_add.is_empty() && self.to_remove.is_empty() &&
+        self.to_inc.is_empty() && self.to_dec.is_empty()
+    }
+}
 
 #[derive(IObj, Debug)]
 pub struct BasicMem<T, OT = T, RT = T, U = u32>
@@ -69,31 +89,31 @@ U: Scalar
 
     pub fn effect_proc(
         es: &Vec<OperationEffect<OT, U>>, mut req: RequestedObj<'_, OT, U>, stop_mux: &Arc<Mutex<bool>>,
-        out_to_add: &mut Vec<PObj<OT, U>>, out_to_remove: &mut Vec<OT>) {
+        out: &mut EPOut<OT, U>) {
         for e in es {
             match e {
                 OperationEffect::CreateObj(f) => {
-                    out_to_add.push(f(&mut req));
+                    out.to_add.push(f(&mut req));
                 },
                 OperationEffect::CreateObjs(f) => {
                     let mut new_o = f(&mut req);
                     while let Some(o) = new_o.pop() {
-                        out_to_add.push(o);
+                        out.to_add.push(o);
                     }
                 },
                 OperationEffect::RemoveObjs(f) => {
                     let mut v = f(&mut req);
                     while let Some(t) = v.pop() {
-                        out_to_remove.push(t);
+                        out.to_remove.push(t);
                     }
                 },
[…]

### 2024-12-03 src/objs.rs

@@ -105,11 +105,10 @@ where T: Clone + Hash + Eq, U: Scalar {
     fn remove_batch_skip(&mut self, ts: &[T]) -> Vec<PObj<T, U>> {
         ts.iter()
         .filter_map(|t| self.instances.remove(t))
-        .map(|o| {
+        .inspect(|o| {
             if let Some(am) = self.amount.get_mut(&o.obj_type().tid) {
                 am.0 -= o.obj_amount();
             }
-            o
         })
         .collect()
     }
@@ -126,18 +125,22 @@ where T: Clone + Hash + Eq, U: Scalar {
 
 impl<T, U> IObjStat<U> for BasicObjStore<T, U>
 where T: Clone + Hash + Eq, U: Scalar {
-    fn amounts(&self) -> impl Iterator<Item = &U> {
-        self.amount.vals().map(|v| &v.0)
-    }
 
     fn tid_at(&self, pos: usize) -> Option<&TypeId> {
         self.amount.get_key(pos)
+    }
+
+    fn type_count(&self) -> usize {
+        self.amount.len()
     }
 
     fn pos_of(&self, ty: &crate::core::ObjType) -> Option<usize> {
         self.amount.index_of(&ty.tid)
     }
 
+    fn amounts(&self) -> impl Iterator<Item = &U> {
+        self.amount.vals().map(|v| &v.0)
+    }
     fn amount_of(&self, ty: &crate::core::ObjType) -> Option<U> {
         self.amount.get(&ty.tid).cloned().map(|v| v.0)
     }
@@ -146,8 +149,16 @@ where T: Clone + Hash + Eq, U: Scalar {
         tys.iter().filter_map(|ty| self.amount.get(&ty.tid).map(|v| &v.0)).collect()
     }
 
-    fn type_count(&self) -> usize {
-        self.amount.len()
+    fn amounts_u(&self) -> impl Iterator<Item = &U> {
+        self.amount.vals().map(|v| &v.1)
+    }
+    
+    fn amount_of_u(&self, ty: &crate::core::ObjType) -> Option<U> {
+        self.amount.get(&ty.tid).cloned().map(|v| v.1)
+    }
+    
+    fn amount_of_many_u(&self, tys: &[crate::core::ObjType]) -> Vec<&U> {
+        tys.iter().filter_map(|ty| self.amount.get(&ty.tid).map(|v| &v.1)).collect()
     }
 }
 
@@ -183,7 +194,7 @@ where T: Clone + Hash + Eq, U: Scalar {
[…]

### 2024-12-03 src/objs/com.rs

@@ -84,6 +84,7 @@ DT: Debug + 'static {
 
 
 
+
 #[derive(IObj, Debug)]
 #[obj_type(TypeGroup::Com)]
 pub struct SChannel<T, U = u32, DT = T> 

### 2024-12-03 src/rules.rs

@@ -44,16 +44,18 @@ where T: Send + Sync + Clone, U: Send + Sync + Clone {
 pub struct BasicCondition<T = u32, U = u32>
 where T: Clone + Hash + Eq, U: Scalar {
     untagged_cond: Option<UntaggedPresences<U>>,
-    tagged_cond: Option<TaggedPresences<T>>
+    tagged_cond: Option<TaggedPresences<T>>,
+    skip_take: bool
 }
 
 impl<T, U> ICondition<T, U> for BasicCondition<T, U>
 where T: Clone + Hash + Eq, U: Scalar {
         
-    fn from_builder(uts: Option<UntaggedPresences<U>>, tgs: Option<TaggedPresences<T>>) -> Self {
+    fn from_builder(uts: Option<UntaggedPresences<U>>, tgs: Option<TaggedPresences<T>>, skip_take: bool) -> Self {
         Self {
             untagged_cond: uts,
             tagged_cond: tgs,
+            skip_take
         }
     }
     
@@ -63,6 +65,10 @@ where T: Clone + Hash + Eq, U: Scalar {
     
     fn tagged(&self) -> &Option<TaggedPresences<T>> {
         &self.tagged_cond
+    }
+    
+    fn skip_take(&self) -> bool {
+        self.skip_take
     }
 
 }

### 2024-12-03 tests/mems/test_mem.rs

@@ -1,9 +1,9 @@
-
+// Copyright 2024 Junshuang Hu
 use std::thread;
 
 use meme::{core::IMem, helpers, mems::basic::BasicMem, objs::com::{ObjChannel, SendMsg, SendWrapper}, rules::{com::SendReceiveRule, BasicCondition, BasicEffect}};
 use meme_derive::*;
-use crate::{objs::{TestObjA, TestObjB}, rules::{TestRuleA, TestRuleB, TestRuleC}};
+use crate::{objs::{TestObjA, TestObjB}, rules::{TestRuleA, TestRuleB, TestRuleC, TestRuleD}};
 
 #[derive(IObj, Debug)]
 pub struct StopObj {
@@ -67,7 +67,8 @@ impl TestComRule {
                     let pobj = Box::new(SendMsg::<i32>::new(helpers::IdGen::next_i32_id(), v));
                     pobj
                 })
-                .crate_obj(|_| Box::new(StopObj { tag: helpers::IdGen::next_i32_id() }))
+                //.crate_obj(|_| Box::new(StopObj { tag: helpers::IdGen::next_i32_id() }))
+                .increase_untagged::<StopObj>(1)
                 .build(),
         }
     }
@@ -92,6 +93,7 @@ pub fn basics() {
             Box::new(SendReceiveRule::new(3, vec![ids[2]])),
             Box::new(TestComRule::new(4, ids[2])),
             Box::new(TestRuleC::new(5)),
+            Box::new(TestRuleD::new(6))
         ]
     );
 

### 2024-12-03 tests/misc/mod.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use std::borrow::Borrow;
 
 use meme::core::{IndexMap, PObj, PRule};

### 2024-12-03 tests/objs/mod.rs

@@ -1,4 +1,4 @@
-
+// Copyright 2024 Junshuang Hu
 use std::any::TypeId;
 
 use meme::core::{IObjStat, ITaggedStore, TypeGroup};

### 2024-12-03 tests/rules/mod.rs

@@ -1,3 +1,4 @@
+// Copyright 2024 Junshuang Hu
 use meme::{core::{IObj, IRuleStat, ITaggedStore}, helpers, objs::BasicObjStore, rules::{BasicCondition, BasicEffect, BasicRuleStore}};
 use meme_derive::{IObj, IRule};
 
@@ -86,6 +87,42 @@ impl TestRuleC {
 
             eff: helpers::effect_builder()
             .crate_obj(|_| Box::new(TestObjC::new(helpers::IdGen::next_i32_id())))
+            .build(),
+        }
+    }
+}
+
+
+#[derive(IObj, IRule, Debug)]
+pub struct TestRuleD {
+    #[tag]
+    t: u32,
+    #[condition]
+    cond: BasicCondition<i32>,
+    #[effect]
+    eff: BasicEffect<i32>
+}
+
+impl TestRuleD {
+    pub fn new(tag: u32) -> Self {
+        Self {
+            t: tag,
+
+            cond: helpers::condition_builder()
+            .rand_tagged::<TestObjC>(1).by_take()
+            .build(),
+
+            eff: helpers::effect_builder()
+            .crate_obj(|req| {
+                assert!(req.take.is_some());
+                if let Some(took) = req.take.as_mut().and_then(|t|t.rand_at_mut(0)) {
+                    assert!(took.len() == 1);
+                    if took.len() != 0 {
+                        return took.pop().unwrap();
+                    }
+                }
+                return Box::new(TestObjC::new(helpers::IdGen::next_i32_id()));
+            })
             .build(),
         }
     }

### 2024-12-09 paper/src/paper.tex
完善自动化脚本
优化图像编译

增加了顶层接口UML图

@@
-% Copyright 2024 Junshuang Hu
+%// Copyright 2024 Junshuang Hu
 \documentclass[9pt,a4paper,twoside]{article}
@@
 \usepackage{amsmath}
-\usepackage{amsfonts}
+\usepackage{amssymb}
 \usepackage{svg}
@@
 
-\newcommand\figpath{../assets/figures/}
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
+\newcommand\figpath{./paper/assets/figures/}
 
@@
                 \begin{equation}
-                    \begin{align}
+                    \begin{aligned}
                         a_{ty} &= Amount_\omega(ty) \\
                         &= \sum_{o \in O'}{Amount(o)} \\
-                    \end{align}
+                    \end{aligned}
                 \end{equation}
@@
             \begin{equation}
-                \begin{align}
+                \begin{aligned}
                     &r(a_1,a_2,...a_n): \\
@@
                     &c_n \rightarrow e_c(c_n)  \\
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
                 e_c=\left\{
-                \begin{align}
+                    \begin{aligned}
                         & i, \forall o_i \in c_t, p_i \subseteq Property(o_i)\\
                         & \epsilon, otherwise
-                \end{align}
-                \right
+                    \end{aligned}
+                \right.
             \end{equation}
@@
             \begin{equation}
-                \begin{align}
+                \begin{aligned}
                     &r_1: \\
@@
                     &(u_2, 20) \rightarrow \epsilon \\
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
              \begin{equation}
-                \begin{align}
+                \begin{aligned}
                     &r_1: \\
@@
                     &(u_2, 20) \rightarrow (u_2, 20) \\
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
             \begin{equation}
-                \begin{align}
+                \begin{aligned}
                     &r_2(a): \\
@@
                     &r_2(a_{old}) \rightarrow \text{Add}(r_2(a = a_{old} + 1))
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
             \begin{equation}
-                \begin{align}
+                \begin{aligned}
                     r_3: o_1,o_2,(u_1, 60) \rightarrow \text{Add}(o_3)\text{Remove}(o_2)
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
             \begin{equation}
-                \begin{align}
+                \begin{aligned}
                     r_4:\epsilon \rightarrow \text{Add}(o_1)\text{Add}(u_1, 1.1)
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
             \begin{equation}
-                \begin{align}
+                \begin{aligned}
                     &r_0: o \rightarrow ca(o,ch_a) \\
                     &r_s: ch_a,ca(o,ch_a) \rightarrow ch_a \\
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
             \begin{equation}
-             \begin{align}
+             \begin{aligned}
                     &r_1: ca(o) \rightarrow o \\
                     &r_r: ch_b(ca) \rightarrow ch_b,ca\\
-                \end{align}
+                \end{aligned}
             \end{equation}
@@
         \subsubsection{Top level interfaces}
-        Objects, rules and membranes are three most important things of a P system.
-Every object, rule or membrane in MEME must implement the corresponding interface IObj, IRule and IMem.
+        Objects, rules and membranes are three most important things of a AGP system, they are abstracted into three interfaces: IObj, IRule and IMem.
+        Every object, rule or membrane in MEME must implement the corresponding interface.
         Interfaces IObjStore and IObjStat are used for the storage and the statistic of objects in the membrane. 
         Similarly, interface IRuleStore and IRuleStat are used for the storage and the statistic of rules in the membrane. 
-These interfaces are the top level interfaces of MEME, their relationship is shown in Figure 4.
+        These interfaces are the top level interfaces of MEME, modules only implemented these interfaces can be combined to form a minimal emulator program as shown in Fig 4.
+        \begin{figure}[!htbp]
+            \centering
+            \includesvg[width=\textwidth]{\figpath minimal_sys.svg}
+            \caption{Minimal emulator system with MEME}
+            \label{fig:fig4}
+        \end{figure}
+
+        Top level interfaces have a dependency relationship, to use a interface in a emulator program, its dependency interface must be used as well,
+        their relationship is shown in Figure 5.
         \begin{figure}[!htbp]
@@
             \caption{Top level interfaces relations of MEME}
-            \label{fig:fig4}
+            \label{fig:fig5}
+        \end{figure}
+
+        IObj, IRule and IMem are defined in the scheme shown in Fig 6 and Fig 7.
+        \begin{figure}[!htbp]
+            \centering
+            \includesvg{\figpath obj.svg}
+            \caption{IObj, IRule and IMem interfaces}
+            \label{fig:fig6}
+        \end{figure}
+        \begin{figure}[!htbp]
+            \centering
+            \includesvg[width=\textwidth]{\figpath rule_mem.svg}
+            \caption{IObj, IRule and IMem interfaces}
+            \label{fig:fig7}
         \end{figure}
@@
         \subsubsection{System architecture}
-        The architecture diagram of MEME is shown in Figure 5.
+        The architecture diagram of a typical emulator system implemented with MEME is shown in Figure 8.
         \begin{figure}[!htbp]
             \centering
-            \includesvg{\figpath placeholder.svg}
+            \includesvg[width=\textwidth]{\figpath sys_arch.svg}
             \caption{Architecture diagram of MEME}
-            \label{fig:fig5}
+            \label{fig:fig8}
         \end{figure}

### 2024-12-11 paper/src/paper.tex
增加了图片
修改了论文

@@
 \usepackage{booktabs} 
+\usepackage{listings}
+\usepackage{xcolor}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=true,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2,
+    frame=tbrl, %t: top, r, b, l 
+    linewidth=\textwidth,
+}
+
+\lstset{style=mystyle}
 
@@
 \newcommand\figpath{./paper/assets/figures/}
+\newcommand\codepath{./paper/src/codes/}
 
@@
         Similarly, interface IRuleStore and IRuleStat are used for the storage and the statistic of rules in the membrane. 
-        These interfaces are the top level interfaces of MEME, modules only implemented these interfaces can be combined to form a minimal emulator program as shown in Fig 4.
-        \begin{figure}[!htbp]
-            \centering
-            \includesvg[width=\textwidth]{\figpath minimal_sys.svg}
-            \caption{Minimal emulator system with MEME}
-            \label{fig:fig4}
-        \end{figure}
+        These interfaces are the top level interfaces of MEME.
 
-        Top level interfaces have a dependency relationship, to use a interface in a emulator program, its dependency interface must be used as well,
-        their relationship is shown in Figure 5.
-        \begin{figure}[!htbp]
-            \centering
-            \includesvg[width=\textwidth]{\figpath interface_relation.svg}
-            \caption{Top level interfaces relations of MEME}
-            \label{fig:fig5}
-        \end{figure}
-
-        IObj, IRule and IMem are defined in the scheme shown in Fig 6 and Fig 7.
+        Objects, rules and membranes are defined in the scheme shown in Figure 4 and Figure 5. Note that, different form its logical structure, instances of objects and rules 
+        can be stored outside of a membrane instance or inside of its properties.
         \begin{figure}[!htbp]
@@
             \caption{IObj, IRule and IMem interfaces}
-            \label{fig:fig6}
+            \label{fig:fig4}
         \end{figure}
@@
             \caption{IObj, IRule and IMem interfaces}
-            \label{fig:fig7}
+            \label{fig:fig5}
         \end{figure}
 
+        Top level interfaces have a dependency relationship, to include a interface in a emulator program, its dependency interface must be included as well,
+        their relationship is shown in Figure 6.
+        \begin{figure}[!htbp]
+            \centering
+            \includesvg[width=\textwidth]{\figpath interface_relation.svg}
+            \caption{Top level interfaces relations of MEME}
+            \label{fig:fig6}
+        \end{figure}
+
+        By using the default modules provided by MEME, a minimal emulator program with one membrane and several objects is written as in 
+        Listing 1.
+
+        \begin{minipage}{\textwidth}
+            \centering
+            \lstinputlisting[language=C++, caption=Code of a minimal emulator program]{\codepath minimal_sys.rs}
+        \end{minipage}
+
         \subsubsection{System architecture}
-        The architecture diagram of a typical emulator system implemented with MEME is shown in Figure 8.
+        The architecture diagram of a typical emulator system implemented with MEME is shown in Figure 7.
         \begin{figure}[!htbp]
@@
             \caption{Architecture diagram of MEME}
-            \label{fig:fig8}
+            \label{fig:fig7}
         \end{figure}

### 2024-12-11 paper/src/codes/minimal_sys.rs

@@ -1,0 +1,56 @@
+// define tagged objects
+#[derive(IObj)]
+struct TA {
+    #[tag]
+    tg: i32,
+    //define unique properties
+    p_1: f32,
+    p_2: f32,
+}
+impl TA {
+    pub fn new(tag: i32, p: [f32;2]) -> Self {
+        Self { 
+            tg: tag,
+            p_1: p[1], p_2: p[2]
+        } 
+    }
+}
+
+// define untagged objects
+struct A;
+struct B;
+struct C;
+
+// define rules
+#[derive(IObj, IRule)]
+pub struct MinimalRule {
+    #[tag]
+    tg: u32,
+    #[condition]
+    cond: BasicCondition<i32>,
+    #[effect]
+    eff: BasicEffect<i32>
+}
+impl MinimalRule {
+    pub fn new(tag: u32) -> Self {
+        Self {
+            tg: tag,
+            cond: helpers::condition_empty(),
+            eff: helpers::effect_empty
+        }
+    }
+}
+
+// program main function
+fn main() {
+    let mut m = BasicMem::<u32, i32>::new(1, false);
+    m.init(
+        vec![
+            Box::new(MinimalTaggedObj::new(2)), 
+        ],
+        vec![
+            Box::new(MinimalRule::new(3)),
+        ]
+    );
+    m.start();
+}

### 2024-12-13 paper/src/paper.tex
更新协议信息
Signed-off-by: Croteco <croteco@outlook.com>
更新了论文，基础膜初始化加入了untagged对象
Signed-off-by: Croteco <croteco@outlook.com>

@@
-%// Copyright 2024 Junshuang Hu
+%Augmented general P systems and high efficiency emulation © 2024 by Junshuang Hu is licensed under Creative Commons Attribution-ShareAlike 4.0 International 
 \documentclass[9pt,a4paper,twoside]{article}
@@
 
-    For the requirement of fast and general emulation for P systems, a emulation library Membrane Emulation Lib (MEME for short) is designed and implemented based on the augmented general P system framework.
+    For the requirement of fast and general emulation for P systems, a emulation library Membrane Emulation Lib (MEME for short) 
+    is designed and implemented based on the augmented general P system framework.
 
-    The current emulation tools take a approach of using a intermediate language, like p-lingua, to describe a P system and compile it into a emulation program, or use it as interpreted language to drive the emulator.
+    The current emulation tools take a approach of using a intermediate language, like p-lingua, 
+    to describe a P system and compile it into a emulation program, or use it as interpreted language to drive the emulator.
 
-    This brings convince for the emulation of the P systems that the intermediate language supports, but when facing a P system that the intermediate language cannot describe, the intermediate language along with its compiler and emulator or the emulation library need to be expanded to adapt the novel system, because the language level of the intermediate language is not high enough.
+    This brings convince for the emulation of the P systems that the intermediate language supports, 
+    since these languages are closer to the mathematical definition of P systems in their forms.
 
-    The structure of the augmented general P system gives a benefit of using mappings to describe the feature of each P systems, these mappings can be implemented directly with modern program languages.
-Hence, not like the current emulation tools, MEME dose not requires a intermediate language to describe a P system, all code is written with program language, therefore MEME can be used to implement more P systems without the update to the library itself.
+    When facing a P system that the intermediate language cannot describe, however,
+    the intermediate language along with its compiler and emulator, or the emulation library, need to be modified to adapt the novel system.
 
-    Another main benefit of MEME is its efficiency.
-With compiled language Rust and multi-thread design, MEME delivers a more efficient program, the implemented P system can be compiled into executable on various platforms.
+    MEME chosed another approach by sacrificing the simplicity of expression, confine the way of defining P systems, to expand the range of systems that
+     it can implement.
+
+    The structure of the augmented general P system gives a benefit of using mappings to describe the feature of each P system, 
+    these mappings can be implemented directly with modern program languages. Hence, not like the current emulation tools,
+     MEME dose not requires a intermediate language to describe a P system, all code is written with program language, 
+     therefore MEME can be used to implement more P systems without the update to the library itself.
+
+    Another main benefit of MEME is its efficiency. With compiled language Rust and multi-thread design,
+     MEME delivers a more efficient program,
+      the implemented P system can be compiled into executable on various compatible platforms without the lose of performance.
 
     \subsection{Structure of MEME}
-    MEME is designed to be a modular library, interfaces between modules and default modules are provided. 
+    MEME is designed to be a modular library, interfaces of modules and default modules are provided. 
+    Modules implemented corresponding interfaces can be combined together to form a emulation program.
     Modules of MEME can be combined with custom modules to expand the function of MEME or to optimize the performance.
+
+    The structure of MEME is as shown in Fig 4. 
+    \begin{figure}[!htbp]
+        \centering
+        \includesvg[width=\textwidth]{\figpath meme_structure.svg}
+        \caption{Structure diagram of MEME}
+        \label{fig:fig4}
+    \end{figure}
 
@@
 
-        Objects, rules and membranes are defined in the scheme shown in Figure 4 and Figure 5. Note that, different form its logical structure, instances of objects and rules 
+        Objects, rules and membranes are defined in the scheme shown in Figure 5 and Figure 6. Note that, different from its logical structure, instances of objects and rules 
         can be stored outside of a membrane instance or inside of its properties.
@@
             \includesvg{\figpath obj.svg}
-            \caption{IObj, IRule and IMem interfaces}
-            \label{fig:fig4}
+            \caption{Objects models}
+            \label{fig:fig5}
         \end{figure}
@@
             \includesvg[width=\textwidth]{\figpath rule_mem.svg}
-            \caption{IObj, IRule and IMem interfaces}
-            \label{fig:fig5}
+            \caption{Rule and membrane models}
+            \label{fig:fig6}
         \end{figure}
@@
         Top level interfaces have a dependency relationship, to include a interface in a emulator program, its dependency interface must be included as well,
-        their relationship is shown in Figure 6.
+        their relationship is shown in Figure 7.
         \begin{figure}[!htbp]
@@
             \caption{Top level interfaces relations of MEME}
-            \label{fig:fig6}
+            \label{fig:fig7}
         \end{figure}
 
-        By using the default modules provided by MEME, a minimal emulator program with one membrane and several objects is written as in 
-        Listing 1.
+        \subsubsection{System architecture}
+        MEME does not provide a fixed program structure for emulators, it only contains a set of convinct modules for implementing AGP systems.
+        By only using MEME modules, the flowchart of a emulator program is shown in Figure 8.
+        \begin{figure}[!htbp]
+            \centering
+            \includesvg{\figpath process.svg}
+            \caption{Flowchart of a MEME based emulator program}
+            \label{fig:fig8}
+        \end{figure}
 
-        \begin{minipage}{\textwidth}
-            \centering
-            \lstinputlisting[language=C++, caption=Code of a minimal emulator program]{\codepath minimal_sys.rs}
-        \end{minipage}
-
-        \subsubsection{System architecture}
-        The architecture diagram of a typical emulator system implemented with MEME is shown in Figure 7.
+        The architecture diagram of a typical emulator system implemented with MEME is shown in Figure 9.
         \begin{figure}[!htbp]
@@
             \includesvg[width=\textwidth]{\figpath sys_arch.svg}
-            \caption{Architecture diagram of MEME}
-            \label{fig:fig7}
+            \caption{Architecture diagram of MEME based emulator system}
+            \label{fig:fig9}
         \end{figure}
 
-    \subsection{Versatility of MEME}
+        \subsubsection{Code Example}
+        By using the default modules provided by MEME, a simple emulator program with one membrane is written as in Listing 1.
+
+        % \begin{minipage}{\textwidth}
+        %     \centering
+        \lstinputlisting[float, language=C++, caption=Code of a simple emulator program]{\codepath minimal_sys.rs}
+        %\end{minipage}
+
+    \subsection{Preconditions of using MEME}
     To use MEME, a P system $sys$ must satisfy the following requirements:
     \begin{itemize}
-        \item $sys$ is defined or has a equivalent definition as a augmented general P system.
+        \item $sys$ is fully or partially defined, or has a equivalent definition, as a augmented general P system.
         \item The feature and effect mappings of $sys$ can be implemented with high-level programming language.

### 2024-12-13 benches/meme_benchmark.rs

@@ -146,6 +146,7 @@ fn criterion_benchmark(c: &mut Criterion<RxxOPS>) {
                     os.push(Box::new(ca));
                     m.init(
                         os,
+                        Default::default(),
                         vec![
                             Box::new(BenchRuleAct::new(helpers::IdGen::next_u32_id(), select_amount)),
                             Box::new(BenchStopRule::new(helpers::IdGen::next_u32_id(), loop_count)),

### 2024-12-13 paper/src/codes/minimal_sys.rs

@@ -1,25 +1,20 @@
+use meme::core::*;
+use meme_derive::*;
+use meme::rules::{BasicCondition, BasicEffect};
+use meme::mems::basic::BasicMem;
+use meme::helpers;
+
 // define tagged objects
 #[derive(IObj)]
 struct TA {
     #[tag]
-    tg: i32,
+    tag: i32,
     //define unique properties
-    p_1: f32,
-    p_2: f32,
-}
-impl TA {
-    pub fn new(tag: i32, p: [f32;2]) -> Self {
-        Self { 
-            tg: tag,
-            p_1: p[1], p_2: p[2]
-        } 
-    }
+    p: f32
 }
 
 // define untagged objects
-struct A;
-struct B;
-struct C;
+struct A;struct B;struct C;
 
 // define rules
 #[derive(IObj, IRule)]
@@ -35,8 +30,9 @@ impl MinimalRule {
     pub fn new(tag: u32) -> Self {
         Self {
             tg: tag,
+            //use helpers to construct condition and effect
             cond: helpers::condition_empty(),
-            eff: helpers::effect_empty
+            eff: helpers::effect_empty()
         }
     }
 }
@@ -45,12 +41,9 @@ impl MinimalRule {
 fn main() {
     let mut m = BasicMem::<u32, i32>::new(1, false);
     m.init(
-        vec![
-            Box::new(MinimalTaggedObj::new(2)), 
-        ],
-        vec![
-            Box::new(MinimalRule::new(3)),
-        ]
+        vec![tagged!(TA{ tag:2, p: 1.1 })],
+        vec![untagged!(A, 10), untagged!(B, 20)],
+        vec![tagged!(MinimalRule::new(3))]
     );
     m.start();
 }

### 2024-12-13 src/core.rs

@@ -160,7 +160,7 @@ pub trait IRule: IObj {
     type Condition: ICondition<Self::ObjTag, Self::ObjUnit>;
     type Effect: IRuleEffect;
     fn condition(&self) -> &Self::Condition;
-    fn effect(&self) -> &Self::Effect; // todo: 令 Effect 只能修改 Condition 选中的对象
+    fn effect(&self) -> &Self::Effect; // todo: 令 Effect 只能修改 Condition 选中的对象 -ok
 }
 
 /// todo: 保证高效实现下的一致性

### 2024-12-13 src/helpers.rs

@@ -244,7 +244,6 @@ pub fn effect_empty<RE: IRuleEffect>() -> RE {
     RE::from_builder(None)
 }
 
-
 // todo: 全局tag生成器 -ok
 
 static COUNTER_USIZE: atomic::AtomicUsize = atomic::AtomicUsize::new(0);
@@ -406,6 +405,19 @@ pub fn vec_batch_remove<T>(v: &mut Vec<T>, indexes: &[usize]) -> Vec<Option<T>> 
     }
     v.truncate(v.len() - valied_removed_count);
     ret
+}
+
+#[macro_export]
+macro_rules! untagged {
+    ($ty:ident, $amount:expr) => (
+        (std::any::TypeId::of::<$ty>(), $amount)
+    )
+}
+#[macro_export]
+macro_rules! tagged {
+    ($expression:expr) => (
+        Box::new($expression)
+    )
 }
 
 /* 

### 2024-12-13 src/mems.rs

@@ -6,3 +6,7 @@ pub mod basic;
 pub struct CPUEnvRegion {
     
 }
+
+pub struct GPUEnvRegion {
+    
+}

### 2024-12-13 src/mems/basic.rs

@@ -77,12 +77,15 @@ U: Scalar
         }
     }
 
-    pub fn init(&mut self, mut objs: Vec<PObj<OT, U>>, mut rules: Vec<PBasicRule<RT, OT, U>>) {
-        while let Some(o) = objs.pop() {
+    pub fn init(&mut self, mut tagged: Vec<PObj<OT, U>>, mut untagged: Vec<(TypeId, U)>, mut rules: Vec<PBasicRule<RT, OT, U>>) {
+        while let Some(o) = tagged.pop() {
             self.objs.add_or_update(o.obj_tag().clone(), o);
         }
         while let Some(r) = rules.pop() {
             self.rules.add_or_update(r.obj_tag().clone(), r);
+        }
+        while let Some((ty, amount)) = untagged.pop() {
+            self.objs.increase(&ty, amount);
         }
         self.ready = true;
     }

### 2024-12-13 tests/mems/test_mem.rs

@@ -1,7 +1,7 @@
 // Copyright 2024 Junshuang Hu
 use std::thread;
 
-use meme::{core::IMem, helpers, mems::basic::BasicMem, objs::com::{ObjChannel, SendMsg, SendWrapper}, rules::{com::SendReceiveRule, BasicCondition, BasicEffect}};
+use meme::{core::IMem, helpers, mems::basic::BasicMem, objs::com::{ObjChannel, SendMsg, SendWrapper}, rules::{com::SendReceiveRule, BasicCondition, BasicEffect}, tagged};
 use meme_derive::*;
 use crate::{objs::{TestObjA, TestObjB}, rules::{TestRuleA, TestRuleB, TestRuleC, TestRuleD}};
 
@@ -82,18 +82,19 @@ pub fn basics() {
     let (ca, cb) = ObjChannel::<i32>::new_pair(ids[2], ids[3]);
     m.init(
         vec![
-            Box::new(TestObjA::new(ids[0], 1.1)), 
-            Box::new(TestObjA::new(ids[1], 2.2)),
-            Box::new(ca)
+            tagged!(TestObjA::new(ids[0], 1.1)), 
+            tagged!(TestObjA::new(ids[1], 2.2)),
+            tagged!(ca)
         ],
+        Default::default(),
         vec![
-            Box::new(TestRuleA::new(0, ids[0])),
-            Box::new(TestRuleB::new(1)),
-            Box::new(TestRuleStop::new(2)),
-            Box::new(SendReceiveRule::new(3, vec![ids[2]])),
-            Box::new(TestComRule::new(4, ids[2])),
-            Box::new(TestRuleC::new(5)),
-            Box::new(TestRuleD::new(6))
+            tagged!(TestRuleA::new(0, ids[0])),
+            tagged!(TestRuleB::new(1)),
+            tagged!(TestRuleStop::new(2)),
+            tagged!(SendReceiveRule::new(3, vec![ids[2]])),
+            tagged!(TestComRule::new(4, ids[2])),
+            tagged!(TestRuleC::new(5)),
+            tagged!(TestRuleD::new(6))
         ]
     );
 
